---
title: "Exploring without the outlier"
output: bookdown::html_document2
---

```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = FALSE)
```

```{r load-all-libraries, message=FALSE, warning=FALSE, results=FALSE}

# Clean the environment
rm(list=ls())

# Load libraries
source('./utils/load_all_libraries.R')

options(dplyr.summarise.inform = FALSE)

# Source other scripts
source('./utils/load_transform_gather.R')

```

# Load and get the datasets ready

```{r load-transform-gather-filter-qc, message=FALSE}

outList <- load_transform_gather()

long_form_data_all_ptp_analyzed <- 
    outList$long_form_data_all_ptp_analyzed
long_form_data_qc_pass_ptp_analyzed <- 
    outList$long_form_data_qc_pass_ptp_analyzed

results_table_all_ptp_analyzed <- 
        outList$results_table_all_ptp_analyzed
results_table_qc_pass_ptp_analyzed <- 
    outList$results_table_qc_pass_ptp_analyzed
results_table_qc_pass_ptp_analyzed_gathered <- 
    outList$results_table_qc_pass_ptp_analyzed_gathered

rm(outList)

```


# Create the dataframes with/without outlier:

```{r get-ses-1-2-with-and-without-the-outlier, message=FALSE, warning=FALSE, results='hide'}

# Calculate the variables for the full data
st_all_data <- 
        long_form_data_qc_pass_ptp_analyzed %>%
        filter(session %in% c(1,2)) %>%
        droplevels() %>%
        group_by(experiment,
                 congruency,
                 arr_phase_1_name,
                 concept_phase_1,
                 ptp,
                 phase,
                 session) %>% 
        summarise(mean = mean(correct, na.rm = TRUE)) %>%
        ungroup()
        
        
        
# Now for no outlier
st_no_outlier <- 
        long_form_data_qc_pass_ptp_analyzed %>%
        filter(session %in% c(1,2)) %>% 
        droplevels() %>%
        filter(prompt_point_idx != 1,
               prompt_point_idx != 5) %>% 
        group_by(experiment,
                 congruency,
                 arr_phase_1_name,
                 concept_phase_1,
                 ptp,
                 phase,
                 session) %>%
        summarise(mean = mean(correct, na.rm = TRUE)) %>%
        ungroup()


# Calculate average for each toy separately
st_by_target <- 
        long_form_data_qc_pass_ptp_analyzed %>%
        filter(session %in% c(1,2)) %>%
        droplevels() %>%
        group_by(experiment,
                 congruency,
                 arr_phase_1_name,
                 concept_phase_1,
                 ptp,
                 phase,
                 session,
                 prompt_img_name) %>%
        summarise(mean = mean(correct, na.rm = TRUE))
        # get_summary_stats(correct,type='mean')

        
```

```{r merge-data-frames}

st <-
        merge(st_all_data,
              st_no_outlier,
              by=c('ptp',
                   'congruency',
                   'concept_phase_1',
                   'phase',
                   'session',
                   'arr_phase_1_name',
                   'experiment'),
              suffixes = c('_all_data',
                           '_no_outlier'),
              all = TRUE)
```

```{r turn-long}
st_long_mean_type <-
        st %>%
        pivot_longer(cols = c(mean_all_data,
                              mean_no_outlier),
                     names_to = 'mean_type',
                     values_to = 'mean_accuracy')

# Now, calculate ses 1 2 average
st_ses_1_2_mean <- 
        st_long_mean_type %>%
        group_by(experiment,
                 congruency,
                 arr_phase_1_name,
                 concept_phase_1,
                 ptp,
                 phase,
                 mean_type) %>%
        summarise(ses_1_2_mean = mean(mean_accuracy, na.rm = TRUE)) %>%
        ungroup() %>%
        mutate(phase = as.character(phase))

st_phase_diff_long <-
        
        st_ses_1_2_mean %>%
        pivot_wider(names_from = phase,
                    names_prefix = 'phase_',
                    values_from = ses_1_2_mean) %>%
        mutate(phase_2_min_phase_1 = phase_2 - phase_1) %>% 
        pivot_longer(cols = c(phase_1,
                              phase_2,
                              phase_2_min_phase_1),
                     names_to = 'phase_type',
                     values_to = 'ses_1_2_mean')

# Ses 1 2 avg for each target
st_by_target_ses_1_2_mean <-
        st_by_target %>%
        group_by(experiment,
                 congruency,
                 arr_phase_1_name,
                 concept_phase_1,
                 ptp,
                 phase,
                 prompt_img_name) %>%
        summarise(ses_1_2_mean = mean(mean, na.rm = TRUE))

# By traget, phase2 min phase1 long form. Only makes sense for the congruent data
st_by_target_phase_diff_long <- 
        st_by_target_ses_1_2_mean %>%
        pivot_wider(names_from = phase,
                    names_prefix = 'phase_',
                    values_from = ses_1_2_mean) %>%
        mutate(phase_2_min_phase_1 = phase_2 - phase_1) %>%
        pivot_longer(cols = c(phase_1,
                              phase_2,
                              phase_2_min_phase_1),
                     names_to = 'phase_type',
                     values_to = 'ses_1_2_mean')        
        


```

# Effect size, with and without an outlier

```{r effect-size-with-without}

st_phase_diff_long %>%
        filter(phase_type == 'phase_2_min_phase_1',
               experiment == 1) %>% 
        group_by(mean_type) %>%
        cohens_d(ses_1_2_mean ~ congruency, 
                 var.equal = FALSE,
                 paired = FALSE, hedges.correction = TRUE)

```


# Plots:

## Overall congruency

Plot the data for congruent and incongruent groups, broken down by:

- Whether its over all data or without the outlier
- Whether its experiment 1 or 2.

Conclusion:
Not much learned from these plots. What is interesting is the arrangement-by-congruency interaction and if thats modulated by exclusion of the outlier. 

```{r congruency-plots, fig.height=6, fig.width=6}

st_phase_diff_long %>%
        filter(phase_type == 'phase_2_min_phase_1') %>% 
        ggplot(aes(x=congruency,y=ses_1_2_mean)) +
        geom_violin() +
        geom_boxplot(notch=TRUE,
                     outlier.shape = NA,
                     width=0.4) +
        geom_jitter(width=0.2,
                    alpha=0.2,
                    height = 0) +
        stat_summary(fun=mean, 
                     geom="point",
                     shape=20, 
                     size=5, 
                     color="blue",
                     fill="blue") +    
        geom_hline(yintercept = 0, linetype = 'dashed') +
        facet_grid(experiment~mean_type,
                   labeller = label_both)

```



## By phase:

Again, we just see what we already knew, with or without the outlier. 
Phase1-2 stayes the same for the incongruent, but increases for the congruent group.

```{r by-phase, fig.height=7, fig.width=9}

st_phase_diff_long %>%
        filter(phase_type != 'phase_2_min_phase_1') %>%
        ggplot(aes(x=phase_type,y=ses_1_2_mean)) +
        geom_violin() +
        geom_boxplot(notch=TRUE,
                     outlier.shape = NA,
                     width=0.4) +
        geom_point(alpha=0.2) +
        geom_line(aes(group=ptp),
                  alpha = 0.2,
                  linetype = 'solid') +
        stat_summary(fun=mean, 
                     geom="point",
                     shape=20, 
                     size=5, 
                     color="blue",
                     fill="blue") +        
        facet_grid(experiment~mean_type+congruency,
                   labeller = label_both)


```

## Overall congruency by arrangements:

For experiment 1:

- We can see the congruency effect disappears for Arr2, when all data is considered. Again, this is because, Arr2-to-Arr1 experiences a boost in performance, due to Sledge-PA1 in Arr1 being very easy.
- We can see the congruncy effect reappears for Arr2, when the outlier is removed. For this plot, when Congruency=1 the data hasn't changed, because then we're dealing with Arr2-to-Arr2, and Arr2 had no "outlier" target. Arr1 had the "outleir" Sledge-PA1. Thus, when Congruency=0, going from Arr2-to-Arr1, the Sledge-PA1 is removed from the Phase2-Arr1 data and the performance drops in Phase 2. Hence, Phase2-minus-Phase1 values drop too.

For experiment 2:

- We can see the congruency effect disappears for Arr3, when all data is considered. Presumably, this is because Arr3-to-Arr4 experiences a boost in performance due to Gingerbread man-PA2 in Arr4 being easy.
- But, excluding the outlier PA does not bring back the congruency effect for Arr3.


```{r by-arr-with-without-outlier, fig.width=10, fig.height=8}

st_phase_diff_long %>%
        filter(phase_type == 'phase_2_min_phase_1') %>%
        ggplot(aes(x=congruency,y=ses_1_2_mean)) +
        geom_violin() +
        geom_boxplot(notch=TRUE,
                     outlier.shape = NA,
                     width=0.4) +
        geom_jitter(width=0.2,
                    alpha=0.2,
                    height = 0) +
        stat_summary(fun=mean, 
                     geom="point",
                     shape=20, 
                     size=5, 
                     color="blue",
                     fill="blue") +  
        geom_hline(yintercept = 0, linetype = 'dashed') +
        facet_grid(mean_type~arr_phase_1_name) + 
        ylab('Phase 2 min Phase 1') +
        ggtitle('Columns are arrangements in phase 1')


```

## By phase and by arrangements:

```{r by-arr-and-phase-with-without-outlier, fig.height=8, fig.width=14}

st_phase_diff_long %>%
        filter(phase_type != 'phase_2_min_phase_1') %>%
        ggplot(aes(x=phase_type,y=ses_1_2_mean)) +
        geom_violin() +
        geom_boxplot(notch=TRUE,
                     outlier.shape = NA,
                     width=0.4) +
        geom_point(alpha=0.2) +
        geom_line(aes(group=ptp),
                  alpha = 0.2,
                  linetype = 'solid') +
        stat_summary(fun=mean, 
                     geom="point",
                     shape=20, 
                     size=5, 
                     color="blue",
                     fill="blue") +        
        facet_grid(mean_type~arr_phase_1_name+congruency,
                   labeller = label_both)


```

## Sanity check plots:

Just plot all_data vs no_outlier for each phase of each group, confirming that the data doesn't change where there is no outlier so all_data==no_outlier, and it does change where the outlier was excluded

```{r sanity-check-plots, fig.height=8, fig.width=14, warning=FALSE, results='hide', message=FALSE}


st_phase_diff_long %>%
        filter(phase_type != 'phase_2_min_phase_1') %>%
        ggplot(aes(x=mean_type,y=ses_1_2_mean)) +
        geom_violin() +
        geom_boxplot(notch=TRUE,
                     outlier.shape = NA,
                     width=0.4) +
        geom_point(alpha=0.2) +
        geom_line(aes(group=ptp),
                  alpha = 0.2,
                  linetype = 'solid') +
        # stat_summary(fun=mean, 
        #              geom="point",
        #              shape=20, 
        #              size=5, 
        #              color="blue",
        #              fill="blue") +        
        facet_grid(congruency~arr_phase_1_name+phase_type,
                   labeller = label_both) +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))












```


# Bayes Factor calculations

We can see that, for experiment 1, starting with Arr2:

- bf_expt_1_arr_2_all_data = 0.39 
- while excluding the outlier bf_expt_1_arr_2_no_outlier = 1.5.

But we also see that for experiment 2, starting with Arr3:

- bf_expt_2_arr_3_all_data = 0.26 
- and is the same for bf_expt_2_arr_2_no_outlier = 0.26



```{r congruency-bf-expt1-all-data}

# Experiment 1: all data
p2_p1_congruent_1_expt_1_all_data <-
    st_phase_diff_long %>%
    filter(experiment == 1,
           congruency == 1,
           mean_type == 'mean_all_data',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

p2_p1_congruent_0_expt_1_all_data <-
    st_phase_diff_long %>%
    filter(experiment == 1,
           congruency == 0,
           mean_type == 'mean_all_data',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

bf_expt_1_all_data <-
    reportBF(ttestBF(
        p2_p1_congruent_1_expt_1_all_data,
        p2_p1_congruent_0_expt_1_all_data,
        paired = FALSE
    ),
    4)

# Experiment 1: all data, arr 1
p2_p1_congruent_1_expt_1_arr_1_all_data <-
    st_phase_diff_long %>%
    filter(experiment == 1,
           congruency == 1,
           arr_phase_1_name == 1,
           mean_type == 'mean_all_data',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

p2_p1_congruent_0_expt_1_arr_1_all_data <-
    st_phase_diff_long %>%
    filter(experiment == 1,
           congruency == 0,
           arr_phase_1_name == 1,
           mean_type == 'mean_all_data',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

bf_expt_1_arr_1_all_data <-
    reportBF(ttestBF(
        p2_p1_congruent_1_expt_1_arr_1_all_data,
        p2_p1_congruent_0_expt_1_arr_1_all_data,
        paired = FALSE
    ),
    4)

# Experiment 1: all data, arr 2
p2_p1_congruent_1_expt_1_arr_2_all_data <-
    st_phase_diff_long %>%
    filter(experiment == 1,
           congruency == 1,
           arr_phase_1_name == 2,
           mean_type == 'mean_all_data',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

p2_p1_congruent_0_expt_1_arr_2_all_data <-
    st_phase_diff_long %>%
    filter(experiment == 1,
           congruency == 0,
           arr_phase_1_name == 2,
           mean_type == 'mean_all_data',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

bf_expt_1_arr_2_all_data <-
    reportBF(ttestBF(
        p2_p1_congruent_1_expt_1_arr_2_all_data,
        p2_p1_congruent_0_expt_1_arr_2_all_data,
        paired = FALSE
    ),
    4)

```



```{r congruency-bf-expt1-no-outlier}
# Experiment 1: no outlier
p2_p1_congruent_1_expt_1_no_outlier <-
    st_phase_diff_long %>%
    filter(experiment == 1,
           congruency == 1,
           mean_type == 'mean_no_outlier',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

p2_p1_congruent_0_expt_1_no_outlier <-
    st_phase_diff_long %>%
    filter(experiment == 1,
           congruency == 0,
           mean_type == 'mean_no_outlier',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

bf_expt_1_no_outlier <-
    reportBF(ttestBF(
        p2_p1_congruent_1_expt_1_no_outlier,
        p2_p1_congruent_0_expt_1_no_outlier,
        paired = FALSE
    ),
    4)


# Experiment 1: no outlier, arr 1
p2_p1_congruent_1_expt_1_arr_1_no_outlier <-
    st_phase_diff_long %>%
    filter(experiment == 1,
           congruency == 1,
           arr_phase_1_name == 1,
           mean_type == 'mean_no_outlier',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

p2_p1_congruent_0_expt_1_arr_1_no_outlier <-
    st_phase_diff_long %>%
    filter(experiment == 1,
           congruency == 0,
           arr_phase_1_name == 1,
           mean_type == 'mean_no_outlier',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

bf_expt_1_arr_1_no_outlier <-
    reportBF(ttestBF(
        p2_p1_congruent_1_expt_1_arr_1_no_outlier,
        p2_p1_congruent_0_expt_1_arr_1_no_outlier,
        paired = FALSE
    ),
    4)

# Experiment 1: no outlier, arr 2
p2_p1_congruent_1_expt_1_arr_2_no_outlier <-
    st_phase_diff_long %>%
    filter(experiment == 1,
           congruency == 1,
           arr_phase_1_name == 2,
           mean_type == 'mean_no_outlier',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

p2_p1_congruent_0_expt_1_arr_2_no_outlier <-
    st_phase_diff_long %>%
    filter(experiment == 1,
           congruency == 0,
           arr_phase_1_name == 2,
           mean_type == 'mean_no_outlier',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

bf_expt_1_arr_2_no_outlier <-
    reportBF(ttestBF(
        p2_p1_congruent_1_expt_1_arr_2_no_outlier,
        p2_p1_congruent_0_expt_1_arr_2_no_outlier,
        paired = FALSE
    ),
    4)

```


```{r congruency-bf-expt2-all-data}

# Experiment 2: all data
p2_p1_congruent_1_expt_2_all_data <-
    st_phase_diff_long %>%
    filter(experiment == 2,
           congruency == 1,
           mean_type == 'mean_all_data',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

p2_p1_congruent_0_expt_2_all_data <-
    st_phase_diff_long %>%
    filter(experiment == 2,
           congruency == 0,
           mean_type == 'mean_all_data',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

bf_expt_2_all_data <-
    reportBF(ttestBF(
        p2_p1_congruent_1_expt_2_all_data,
        p2_p1_congruent_0_expt_2_all_data,
        paired = FALSE
    ),
    4)

# Experiment 2: all data, arr 3
p2_p1_congruent_1_expt_2_arr_3_all_data <-
    st_phase_diff_long %>%
    filter(experiment == 2,
           congruency == 1,
           arr_phase_1_name == 3,
           mean_type == 'mean_all_data',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

p2_p1_congruent_0_expt_2_arr_3_all_data <-
    st_phase_diff_long %>%
    filter(experiment == 2,
           congruency == 0,
           arr_phase_1_name == 3,
           mean_type == 'mean_all_data',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

bf_expt_2_arr_3_all_data <-
    reportBF(ttestBF(
        p2_p1_congruent_1_expt_2_arr_3_all_data,
        p2_p1_congruent_0_expt_2_arr_3_all_data,
        paired = FALSE
    ),
    4)

# Experiment 2: all data, arr 4
p2_p1_congruent_1_expt_2_arr_4_all_data <-
    st_phase_diff_long %>%
    filter(experiment == 2,
           congruency == 1,
           arr_phase_1_name == 4,
           mean_type == 'mean_all_data',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

p2_p1_congruent_0_expt_2_arr_4_all_data <-
    st_phase_diff_long %>%
    filter(experiment == 2,
           congruency == 0,
           arr_phase_1_name == 4,
           mean_type == 'mean_all_data',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

bf_expt_2_arr_4_all_data <-
    reportBF(ttestBF(
        p2_p1_congruent_1_expt_2_arr_4_all_data,
        p2_p1_congruent_0_expt_2_arr_4_all_data,
        paired = FALSE
    ),
    4)

```



```{r congruency-bf-expt2-no-outlier}

# Experiment 2: no outlier
p2_p1_congruent_1_expt_2_no_outlier <-
    st_phase_diff_long %>%
    filter(experiment == 2,
           congruency == 1,
           mean_type == 'mean_no_outlier',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

p2_p1_congruent_0_expt_2_no_outlier <-
    st_phase_diff_long %>%
    filter(experiment == 2,
           congruency == 0,
           mean_type == 'mean_no_outlier',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

bf_expt_2_no_outlier <-
    reportBF(ttestBF(
        p2_p1_congruent_1_expt_2_no_outlier,
        p2_p1_congruent_0_expt_2_no_outlier,
        paired = FALSE
    ),
    4)

# Experiment 2: no outlier, arr 3
p2_p1_congruent_1_expt_2_arr_3_no_outlier <-
    st_phase_diff_long %>%
    filter(experiment == 2,
           congruency == 1,
           arr_phase_1_name == 3,
           mean_type == 'mean_no_outlier',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

p2_p1_congruent_0_expt_2_arr_3_no_outlier <-
    st_phase_diff_long %>%
    filter(experiment == 2,
           congruency == 0,
           arr_phase_1_name == 3,
           mean_type == 'mean_no_outlier',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

bf_expt_2_arr_3_no_outlier <-
    reportBF(ttestBF(
        p2_p1_congruent_1_expt_2_arr_3_no_outlier,
        p2_p1_congruent_0_expt_2_arr_3_no_outlier,
        paired = FALSE
    ),
    4)

# Experiment 2: no outlier, arr 4
p2_p1_congruent_1_expt_2_arr_4_no_outlier <-
    st_phase_diff_long %>%
    filter(experiment == 2,
           congruency == 1,
           arr_phase_1_name == 4,
           mean_type == 'mean_no_outlier',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

p2_p1_congruent_0_expt_2_arr_4_no_outlier <-
    st_phase_diff_long %>%
    filter(experiment == 2,
           congruency == 0,
           arr_phase_1_name == 4,
           mean_type == 'mean_no_outlier',
           phase_type == 'phase_2_min_phase_1') %>%
    select(ses_1_2_mean) %>% .[[1]]

bf_expt_2_arr_4_no_outlier <-
    reportBF(ttestBF(
        p2_p1_congruent_1_expt_2_arr_4_no_outlier,
        p2_p1_congruent_0_expt_2_arr_4_no_outlier,
        paired = FALSE
    ),
    4)

```

## List all the BFs

### Experiment 1:

bf_expt_1_all_data = `r bf_expt_1_all_data`

bf_expt_1_no_outlier = `r bf_expt_1_no_outlier`

bf_expt_1_arr_1_all_data = `r bf_expt_1_arr_1_all_data`

bf_expt_1_arr_1_no_outlier = `r bf_expt_1_arr_1_no_outlier`

bf_expt_1_arr_2_all_data = `r bf_expt_1_arr_2_all_data`

bf_expt_1_arr_2_no_outlier = `r bf_expt_1_arr_2_no_outlier`


### Experiment 2:

bf_expt_2_all_data = `r bf_expt_2_all_data`

bf_expt_2_no_outlier = `r bf_expt_2_no_outlier`

bf_expt_2_arr_3_all_data = `r bf_expt_2_arr_3_all_data`

bf_expt_2_arr_3_no_outlier = `r bf_expt_2_arr_3_no_outlier`

bf_expt_2_arr_4_all_data = `r bf_expt_2_arr_4_all_data`

bf_expt_2_arr_4_no_outlier = `r bf_expt_2_arr_4_no_outlier`

