---
title: "various_analyses"
output: bookdown::html_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load-all-libraries, message=FALSE, warning=FALSE, results=FALSE}

# Clean the environment
rm(list=ls())

# Load libraries
library(tidyverse)
library(readxl)
library(ggpubr)
library(rstatix)
library(emmeans)
library(BayesFactor)
library(DT)
library(kableExtra)
library(assortedRFunctions)
library(TOSTER)
library(gridExtra)

# Source other scripts
source('./utils/load_transform_gather.R')

```

# Load and get the datasets ready

```{r load-transform-gather-filter-qc}

outList <- load_transform_gather()

long_form_data_all_ptp <- 
    outList$long_form_data_all_ptp

long_form_data_qc_pass_ptp <- 
    outList$long_form_data_qc_pass_ptp

results_table_qc_pass_ptp_analyzed <- 
    outList$results_table_qc_pass_ptp_analyzed
results_table_qc_pass_ptp_analyzed_gathered <- 
    outList$results_table_qc_pass_ptp_analyzed_gathered

rm(outList)

```

# Bayesian ANOVA analysis

## Bayesian ANOVA for both experiments combined

```{r various-analyses-1 }

# Basic summary table
results_table_qc_pass_ptp_analyzed %>%
        group_by(arr_phase_1_1,congruency) %>%
        get_summary_stats(phase_2_min_phase_1_ses_1_2_perf, type = 'mean_sd') %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")

# bf_both_expt <- anovaBF(phase_2_min_phase_1_ses_1_2_perf~
#                             congruency*
#                             concept_phase_1*
#                             phase_1_lower_left_outlier*
#                             arrangement_pairs, 
#              data = results_table_qc_pass_ptp_analyzed,
#              whichModels="withmain",
#              whichRandom = "ptp", iterations = 100000)
# 
# bf_both_expt <- sort(bf_both_expt, decreasing = TRUE)
# 
# bf_both_expt %>% knitr::kable() %>%
#         kable_styling(bootstrap_options = "striped")

```

## Bayesian ANOVA for arr1-2

```{r various-analyses-2 }

# results_table_arr_1_2 <- results_table_qc_pass_ptp_analyzed %>%
#         filter(arr_phase_1_1 == 1 | arr_phase_1_1 == 14)
# 
# bf_arr_1_2 <- anovaBF(phase_2_min_phase_1_ses_1_2_perf~
#                               congruency*
#                               concept_phase_1*
#                               arr_phase_1_1, 
#              data = results_table_arr_1_2,
#              whichModels="withmain",
#              whichRandom = "ptp", iterations = 100000)
# 
# bf_arr_1_2 <- sort(bf_arr_1_2, decreasing = TRUE)
# 
# bf_arr_1_2 %>% knitr::kable() %>%
#         kable_styling(bootstrap_options = "striped")

```

## Bayesian ANOVA for arr3-4

```{r various-analyses-3 }

# results_table_arr_3_4 <- results_table_qc_pass_ptp_analyzed %>%
#         filter(arr_phase_1_1 == 3 | arr_phase_1_1 == 15)
# 
# bf_arr_3_4 <- anovaBF(phase_2_min_phase_1_ses_1_2_perf~
#                               congruency*
#                               concept_phase_1*
#                               arr_phase_1_1, 
#              data = results_table_arr_3_4,
#              whichModels="withmain",
#              whichRandom = "ptp", iterations = 100000)
# 
# bf_arr_3_4 <- sort(bf_arr_3_4, decreasing = TRUE)
# 
# bf_arr_3_4 %>% knitr::kable() %>% 
#         kable_styling(bootstrap_options = "striped")


```

# Bayesian t-test analysis

## For arr1-2

```{r various-analyses-4}
# 
# # Analyze session differences
# arr1_2_ses_1_2_perf_congruent_1 <- results_table_arr_1_2 %>%
#         filter(congruency == 1) %>%
#         select(phase_2_min_phase_1_ses_1_2_perf) %>%
#         .[[1]]
# arr1_2_ses_1_2_perf_congruent_0 <- results_table_arr_1_2 %>%
#         filter(congruency == 0) %>%
#         select(phase_2_min_phase_1_ses_1_2_perf) %>%
#         .[[1]]
# 
# arr1_2_bf_ses_1_2_perf <-
#     reportBF(ttestBF(
#         arr1_2_ses_1_2_perf_congruent_1,
#         arr1_2_ses_1_2_perf_congruent_0,
#         paired = FALSE
#     ),
#     4)
# 
# arr1_2_bf_ses_1_2_perf
# 
# # Normal t-test?
# t.test(arr1_2_ses_1_2_perf_congruent_0,arr1_2_ses_1_2_perf_congruent_1,paired=FALSE)
```
The BF for t-test matches the congruency main effect reported by the Bayesian ANOVA.

## For arr3-4
```{r various-analyses-5}
# # Analyze session differences
# arr3_4_ses_1_2_perf_congruent_1 = results_table_arr_3_4 %>%
#         filter(congruency == 1) %>%
#         select(phase_2_min_phase_1_ses_1_2_perf) %>%
#         .[[1]]
# arr3_4_ses_1_2_perf_congruent_0 = results_table_arr_3_4 %>%
#         filter(congruency == 0) %>%
#         select(phase_2_min_phase_1_ses_1_2_perf) %>%
#         .[[1]]
# 
# arr3_4_bf_ses_1_2_perf <-
#     reportBF(ttestBF(
#         arr3_4_ses_1_2_perf_congruent_1,
#         arr3_4_ses_1_2_perf_congruent_0,
#         paired = FALSE
#     ),
#     4)
# 
# arr3_4_bf_ses_1_2_perf
# 
# # Normal t-test?
# t.test(arr3_4_ses_1_2_perf_congruent_0,arr3_4_ses_1_2_perf_congruent_1,paired=FALSE)
```
The BF for t-test matches the congruency main effect reported by the Bayesian ANOVA.


## Impact of the lower-left outlier

### Bayesian ANOVA for phase 2 always having arr3

```{r anova-bayes-for-arr3-in-phase2}

# results_table_arr_3_in_phase_2 <- results_table_qc_pass_ptp_analyzed %>%
#         filter(arr_phase_2_1 == 3)
# 
# bf_arr_3_in_phase_2 <- anovaBF(phase_2_min_phase_1_ses_1_2_perf~
#                               congruency*
#                               concept_phase_1, 
#              data = results_table_arr_3_in_phase_2,
#              whichModels="withmain",
#              whichRandom = "ptp", iterations = 100000)
# 
# bf_arr_3_in_phase_2 <- sort(bf_arr_3_in_phase_2, decreasing = TRUE)
# 
# bf_arr_3_in_phase_2 %>% knitr::kable() %>%
#         kable_styling(bootstrap_options = "striped")
# 


```

### Bayesian t-test for arr3 always in phase 2

```{r ttest-bayes-arr3_in_phase2}

# # Analyze session differences
# results_table_arr_3_in_phase_2_congruent_1 <- results_table_arr_3_in_phase_2 %>%
#         filter(congruency == 1) %>%
#         select(phase_2_min_phase_1_ses_1_2_perf) %>%
#         .[[1]]
#         
# results_table_arr_3_in_phase_2_congruent_0 <- results_table_arr_3_in_phase_2 %>%
#         filter(congruency == 0) %>%
#         select(phase_2_min_phase_1_ses_1_2_perf) %>%
#         .[[1]]
# 
# arr3_in_phase_2_bf_ses_1_2_perf <-
#     reportBF(ttestBF(
#         results_table_arr_3_in_phase_2_congruent_1,
#         results_table_arr_3_in_phase_2_congruent_0,
#         paired = FALSE
#     ),
#     4)
# 
# arr3_in_phase_2_bf_ses_1_2_perf
# 
# # Normal t-test?
# t.test(results_table_arr_3_in_phase_2_congruent_0,results_table_arr_3_in_phase_2_congruent_1,paired=FALSE)
```


