---
title: "sliceAndDicePlots"
output: bookdown::html_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load-all-libraries, message=FALSE, warning=FALSE, results=FALSE}

# Clean the environment
rm(list=ls())

# Load libraries
library(tidyverse)
library(readxl)
library(ggpubr)
library(rstatix)
library(emmeans)
library(BayesFactor)
library(DT)
library(kableExtra)
library(assortedRFunctions)
library(TOSTER)

# Source other scripts
source('./utils/load_transform_gather.R')

```

# Load and get the datasets ready

```{r load-transform-gather-filter-qc}

outList <- load_transform_gather()

long_form_data_all_ptp <- 
    outList$long_form_data_all_ptp

long_form_data_qc_pass_ptp <- 
    outList$long_form_data_qc_pass_ptp

results_table_qc_pass_ptp_analyzed <- 
    outList$results_table_qc_pass_ptp_analyzed
results_table_qc_pass_ptp_analyzed_gathered <- 
    outList$results_table_qc_pass_ptp_analyzed_gathered

rm(outList)

```

# Plots for experiment 1:

## The Basic congruency effect:

```{r congruency-effect-expt-1, fig.width=5}

results_table_qc_pass_ptp_analyzed %>%
        filter(arrangement_pairs=='arr_1_2') %>%
        ggplot(aes(x=congruency,
                   y=phase_2_min_phase_1_ses_1_2_perf,
                   fill=congruency)) + 
        geom_boxplot(width=0.2,notch = TRUE,outlier.shape = NA) + 
        # geom_point(pch=21,
        #            position = position_jitterdodge(dodge.width=0.5,
        #                                            jitter.width=0.1)) +
        geom_dotplot(binaxis='y', stackdir='center',
                     stackratio=1, dotsize=0.7, fill="black") +
        stat_summary(fun=mean, geom="point", shape=20, size=5, color="red", fill="red") +    
        ylab("Plase 2 - Phase 1") + 
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10)) +
        scale_x_discrete(labels=c('Incongruent','Congruent')) +
        scale_fill_manual(values=c('#e5f5f9','#2ca25f')) + 
        theme(legend.position="none",
              axis.title.x=element_blank())

# Basic summary table
results_table_qc_pass_ptp_analyzed %>%
        filter(arrangement_pairs == 'arr_1_2') %>%
        group_by(congruency) %>%
        get_summary_stats(phase_2_min_phase_1_ses_1_2_perf, type = 'mean_sd') %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")

# Bayes factor analysis:

# Analyze session differences
ses_1_2_perf_congruent_1_arr_1_2 <-
    results_table_qc_pass_ptp_analyzed %>%
    filter(arrangement_pairs == 'arr_1_2' & congruency == 1) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]

ses_1_2_perf_congruent_0_arr_1_2 <-
    results_table_qc_pass_ptp_analyzed %>%
    filter(arrangement_pairs == 'arr_1_2' & congruency == 0) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]

bf_ses_1_2_perf_arr_1_2 <-
    reportBF(ttestBF(
        ses_1_2_perf_congruent_1_arr_1_2,
        ses_1_2_perf_congruent_0_arr_1_2,
        paired = FALSE
    ),
    4)

# Basic t-test
t.test(ses_1_2_perf_congruent_0_arr_1_2,ses_1_2_perf_congruent_1_arr_1_2,paired=FALSE)

# Effect size for the session differences
sd_c1 <- sd(ses_1_2_perf_congruent_1_arr_1_2)
sd_c0 <- sd(ses_1_2_perf_congruent_0_arr_1_2)

n_c1 <- length(ses_1_2_perf_congruent_1_arr_1_2)
n_c0 <- length(ses_1_2_perf_congruent_0_arr_1_2)

pooled_sd <- sqrt( 
    (
    (n_c1-1)*(sd_c1^2) + 
    (n_c0-1)*(sd_c0^2)
    ) / (n_c1 + n_c0 - 2)
    )

effect_size_arr_1_2 <- (mean(ses_1_2_perf_congruent_1_arr_1_2) - mean(ses_1_2_perf_congruent_0_arr_1_2)) /
    pooled_sd

```
## The basic congruency effect, broken in phases

```{r congruency-effect-expt-1-by-phases}
results_table_qc_pass_ptp_analyzed_gathered %>% 
        filter(arrangement_pairs == 'arr_1_2') %>%
        ggplot(aes(x=congruency,
                   y=ses_1_2_perf,
                   fill=phase)) +
        geom_boxplot(width=0.5,notch=TRUE,outlier.shape = NA) + 
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.05)) +
        ylab("Percent correct in sessions 1&2") + 
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10),
              axis.title.x=element_blank(),
              legend.position = 'top') + 
        scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                          name=element_blank(),
                          labels=c('Phase 1','Phase 2')) + 
        scale_x_discrete(labels=c('Incongruent','Congruent'))

# Basic summary table
results_table_qc_pass_ptp_analyzed_gathered %>%
        filter(arrangement_pairs == 'arr_1_2') %>%
        group_by(congruency,phase) %>%
        get_summary_stats(ses_1_2_perf, type = 'mean_sd') %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")
```
## The Basic congruency effect, arrangement order:

```{r congruency-effect-expt-1-by-arrangements, fig.width=5}

results_table_qc_pass_ptp_analyzed %>%
        filter(arrangement_pairs=='arr_1_2') %>%
        ggplot(aes(x=congruency,
                   y=phase_2_min_phase_1_ses_1_2_perf,
                   fill=congruency)) + 
        geom_boxplot(width=0.5,notch = TRUE,outlier.shape = NA) + 
        # geom_point(pch=21,
        #            position = position_jitterdodge(dodge.width=0.5,
        #                                            jitter.width=0.1)) +
        geom_dotplot(binaxis='y', stackdir='center',
                     stackratio=1, dotsize=0.7, fill="black") +
        stat_summary(fun=mean, geom="point", shape=20, size=5, color="red", fill="red") +    
        ylab("Plase 2 - Phase 1") + 
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10)) +
        scale_x_discrete(labels=c('Incongruent','Congruent')) +
        scale_fill_manual(values=c('#e5f5f9','#2ca25f')) + 
        theme(legend.position="none",
              axis.title.x=element_blank()) + 
        facet_wrap(~arr_phase_1_1,
                   labeller = labeller(arr_phase_1_1 = c("1" = "Start with Arr1",
                                                         "14" = "Start with Arr2")))

# Basic summary table
results_table_qc_pass_ptp_analyzed %>%
        filter(arrangement_pairs == 'arr_1_2') %>%
        group_by(arr_phase_1_1,congruency) %>%
        get_summary_stats(phase_2_min_phase_1_ses_1_2_perf, type = 'mean_sd') %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")

# Bayes factor analysis

data_arr_1_c1 <- results_table_qc_pass_ptp_analyzed %>%
    filter(arr_phase_1_1 == 1 & congruency == 1) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]
data_arr_1_c0 <- results_table_qc_pass_ptp_analyzed %>%
    filter(arr_phase_1_1 == 1 & congruency == 0) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]
data_arr_2_c1 <- results_table_qc_pass_ptp_analyzed %>%
    filter(arr_phase_1_1 == 14 & congruency == 1) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]
data_arr_2_c0 <- results_table_qc_pass_ptp_analyzed %>%
    filter(arr_phase_1_1 == 14 & congruency == 0) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]

# Run the bayesian analysis

BF_arr_1_first <- ttestBF(
    data_arr_1_c1,data_arr_1_c0,    
    paired = FALSE
) %>% reportBF(4)
BF_arr_2_first <- ttestBF(
    data_arr_2_c1,
    data_arr_2_c0,    
    paired = FALSE
) %>% reportBF(4)


```
## The basic congruency effect, broken in phases, arrangement order

```{r congruency-effect-expt-1-by-phases-by-arrangements}
results_table_qc_pass_ptp_analyzed_gathered %>% 
        filter(arrangement_pairs == 'arr_1_2') %>%
        ggplot(aes(x=congruency,
                   y=ses_1_2_perf,
                   fill=phase)) +
        geom_boxplot(width=0.5,notch=TRUE,outlier.shape = NA) + 
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.05)) +
        ylab("Percent correct in sessions 1&2") + 
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10),
              axis.title.x=element_blank(),
              legend.position = 'top') + 
        scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                          name=element_blank(),
                          labels=c('Phase 1','Phase 2')) + 
        scale_x_discrete(labels=c('Incongruent','Congruent')) + 
        facet_wrap(~arr_phase_1_1,
                   labeller = labeller(arr_phase_1_1 = c("1" = "Start with Arr1",
                                                 "14" = "Start with Arr2")))

# Basic summary table
results_table_qc_pass_ptp_analyzed_gathered %>%
        group_by(arrangement_pairs,congruency,phase) %>%
        get_summary_stats(ses_1_2_perf, type = 'mean_sd') %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")
```


## Look at performance for individual toys

```{r individual-targets-incongruent-expt-1, fig.height = 5, fig.width = 10}

# Filter to have only sessions 1-2, only incongruent, phase, arrangement, and the target that was the prompt for the trial

long_form_data_qc_pass_ptp %>%
        filter(arrangement_pairs == 'arr_1_2' & 
                   (session == 1 | session == 2) & 
                   congruency == 0) %>%
        select(congruency,arr_phase_1_1,arr_phase_2_1,
               current_arrangement,concept_phase_1,ptp,
               phase,session,prompt_img_name,correct) %>%
        reorder_levels(prompt_img_name, 
                       order = c("Sledge", "Gingerman", "Bear")) %>%
        reorder_levels(current_arrangement,
                       order = c('1','14')) %>%
        group_by(current_arrangement,ptp,phase,prompt_img_name) %>%
        summarize(avg_correct = mean(correct, na.rm = TRUE)) %>%
        ggplot(aes(x=current_arrangement,fill=prompt_img_name, y=avg_correct)) +
        geom_violin() +
        stat_summary(fun=mean, geom="point", shape=19, size=2, 
                     position=position_dodge(0.9)) +
        stat_summary(fun=median, geom="point", shape=6, size=2, position=position_dodge(0.9)) +
        facet_wrap(~phase, labeller =
                           labeller(phase = c("1" = "Phase 1","2" = "Phase 2"))) +
        theme(
                legend.position="top",
                legend.title=element_blank(),
                plot.title = element_text(size=11),
                axis.title.x=element_blank()
                ) + 
        scale_x_discrete(labels=c('Arr1','Arr2')) +
        ylab('% Correct Sessions 1&2')
        

```


# Plots for experiment 2:

## The Basic congruency effect:

```{r congruency-effect-expt-2, fig.width=5}

results_table_qc_pass_ptp_analyzed %>%
        filter(arrangement_pairs=='arr_3_4') %>%
        ggplot(aes(x=congruency,
                   y=phase_2_min_phase_1_ses_1_2_perf,
                   fill=congruency)) + 
        geom_boxplot(width=0.3,notch = TRUE,outlier.shape = NA) + 
        # geom_point(pch=21,
        #            position = position_jitterdodge(dodge.width=0.5,
        #                                            jitter.width=0.1)) +
        geom_dotplot(binaxis='y', stackdir='center',
                     stackratio=1, dotsize=0.7, fill="black") +
        stat_summary(fun=mean, geom="point", shape=20, size=5, color="red", fill="red") +    
        ylab("Plase 2 - Phase 1") + 
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10)) +
        scale_x_discrete(labels=c('Incongruent','Congruent')) +
        scale_fill_manual(values=c('#e5f5f9','#2ca25f')) + 
        theme(legend.position="none",
              axis.title.x=element_blank())

# Basic summary table
results_table_qc_pass_ptp_analyzed %>%
        filter(arrangement_pairs == 'arr_3_4') %>%
        group_by(congruency) %>%
        get_summary_stats(phase_2_min_phase_1_ses_1_2_perf, type = 'mean_sd') %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")

# Bayes factor analysis:

# Analyze session differences
ses_1_2_perf_congruent_1_arr_3_4 <-
    results_table_qc_pass_ptp_analyzed %>%
    filter(arrangement_pairs == 'arr_3_4' & congruency == 1) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]

ses_1_2_perf_congruent_0_arr_3_4 <-
    results_table_qc_pass_ptp_analyzed %>%
    filter(arrangement_pairs == 'arr_3_4' & congruency == 0) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]

bf_ses_1_2_perf_arr_3_4 <-
    reportBF(ttestBF(
        ses_1_2_perf_congruent_1_arr_3_4,
        ses_1_2_perf_congruent_0_arr_3_4,
        paired = FALSE
    ),
    4)

# Basic t-test
t.test(ses_1_2_perf_congruent_0_arr_3_4,
       ses_1_2_perf_congruent_1_arr_3_4,
       paired=FALSE)

# Effect size for the session differences
sd_c1 <- sd(ses_1_2_perf_congruent_1_arr_3_4)
sd_c0 <- sd(ses_1_2_perf_congruent_0_arr_3_4)

n_c1 <- length(ses_1_2_perf_congruent_1_arr_3_4)
n_c0 <- length(ses_1_2_perf_congruent_0_arr_3_4)

pooled_sd <- sqrt( 
    (
    (n_c1-1)*(sd_c1^2) + 
    (n_c0-1)*(sd_c0^2)
    ) / (n_c1 + n_c0 - 2)
    )

effect_size_arr_3_4 <- (mean(ses_1_2_perf_congruent_1_arr_3_4) - mean(ses_1_2_perf_congruent_0_arr_3_4)) /
    pooled_sd

```
## The basic congruency effect, broken in phases

```{r congruency-effect-expt-2-by-phases}
results_table_qc_pass_ptp_analyzed_gathered %>% 
        filter(arrangement_pairs == 'arr_3_4') %>%
        ggplot(aes(x=congruency,
                   y=ses_1_2_perf,
                   fill=phase)) +
        geom_boxplot(width=0.5,notch=TRUE,outlier.shape = NA) + 
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.05)) +
        ylab("Percent correct in sessions 1&2") + 
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10),
              axis.title.x=element_blank(),
              legend.position = 'top') + 
        scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                          name=element_blank(),
                          labels=c('Phase 1','Phase 2')) + 
        scale_x_discrete(labels=c('Incongruent','Congruent'))

# Basic summary table
results_table_qc_pass_ptp_analyzed_gathered %>%
        filter(arrangement_pairs == 'arr_3_4') %>%
        group_by(congruency,phase) %>%
        get_summary_stats(ses_1_2_perf, type = 'mean_sd') %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")

```
## The Basic congruency effect, arrangement order:

```{r congruency-effect-expt-2-by-arrangements, fig.width=5}

results_table_qc_pass_ptp_analyzed %>%
        filter(arrangement_pairs=='arr_3_4') %>%
        ggplot(aes(x=congruency,
                   y=phase_2_min_phase_1_ses_1_2_perf,
                   fill=congruency)) + 
        geom_boxplot(width=0.5,notch = TRUE,outlier.shape = NA) + 
        # geom_point(pch=21,
        #            position = position_jitterdodge(dodge.width=0.5,
        #                                            jitter.width=0.1)) +
        geom_dotplot(binaxis='y', stackdir='center',
                     stackratio=1, dotsize=0.7, fill="black") +
        stat_summary(fun=mean, geom="point", shape=20, size=5, color="red", fill="red") +    
        ylab("Plase 2 - Phase 1") + 
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10)) +
        scale_x_discrete(labels=c('Incongruent','Congruent')) +
        scale_fill_manual(values=c('#e5f5f9','#2ca25f')) + 
        theme(legend.position="none",
              axis.title.x=element_blank()) + 
        facet_wrap(~arr_phase_1_1,
                   labeller = labeller(arr_phase_1_1 = c("3" = "Start with Arr3",
                                                         "15" = "Start with Arr4")))

# Basic summary table
results_table_qc_pass_ptp_analyzed %>%
        filter(arrangement_pairs == 'arr_3_4') %>%
        group_by(congruency,arr_phase_1_1) %>%
        get_summary_stats(phase_2_min_phase_1_ses_1_2_perf, type = 'mean_sd') %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")

# Bayes factor analysis

data_arr_3_c1 <- results_table_qc_pass_ptp_analyzed %>%
    filter(arr_phase_1_1 == 3 & congruency == 1) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]
data_arr_3_c0 <- results_table_qc_pass_ptp_analyzed %>%
    filter(arr_phase_1_1 == 3 & congruency == 0) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]
data_arr_4_c1 <- results_table_qc_pass_ptp_analyzed %>%
    filter(arr_phase_1_1 == 15 & congruency == 1) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]
data_arr_4_c0 <- results_table_qc_pass_ptp_analyzed %>%
    filter(arr_phase_1_1 == 15 & congruency == 0) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]

# Run the bayesian analysis
BF_arr_3_first <- ttestBF(
    data_arr_3_c1,
    data_arr_3_c0,    
    paired = FALSE
) %>% reportBF(4)
BF_arr_4_first <- ttestBF(
    data_arr_4_c1,
    data_arr_4_c0,    
    paired = FALSE
) %>% reportBF(4)


```
## The basic congruency effect, broken in phases, arrangement order

```{r congruency-effect-expt-2-by-phases-by-arrangements}
results_table_qc_pass_ptp_analyzed_gathered %>% 
        filter(arrangement_pairs == 'arr_3_4') %>%
        ggplot(aes(x=congruency,
                   y=ses_1_2_perf,
                   fill=phase)) +
        geom_boxplot(width=0.5,notch=TRUE,outlier.shape = NA) + 
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.05)) +
        ylab("Percent correct in sessions 1&2") + 
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10),
              axis.title.x=element_blank(),
              legend.position = 'top') + 
        scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                          name=element_blank(),
                          labels=c('Phase 1','Phase 2')) + 
        scale_x_discrete(labels=c('Incongruent','Congruent')) + 
        facet_wrap(~arr_phase_1_1,
                   labeller = labeller(arr_phase_1_1 = c("3" = "Start with Arr3",
                                                 "15" = "Start with Arr4")))

# Basic summary table
results_table_qc_pass_ptp_analyzed_gathered %>%
        group_by(congruency,phase,arr_phase_1_1) %>%
        get_summary_stats(ses_1_2_perf, type = 'mean_sd') %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")
```


## Look at performance for individual toys

```{r individual-targets-incongruent-expt-2, fig.height = 5, fig.width = 10}

# Filter to have only sessions 1-2, only incongruent, phase, arrangement, and the target that was the prompt for the trial

long_form_data_qc_pass_ptp %>%
        filter(arrangement_pairs == 'arr_3_4' & 
                   (session == 1 | session == 2) & 
                   congruency == 0) %>%
        select(congruency,arr_phase_1_1,arr_phase_2_1,
               current_arrangement,concept_phase_1,ptp,
               phase,session,prompt_img_name,correct) %>%
        reorder_levels(prompt_img_name, 
                       order = c("Sledge", "Gingerman", "Bear")) %>%
        reorder_levels(current_arrangement,
                       order = c('3','15')) %>%
        group_by(current_arrangement,ptp,phase,prompt_img_name) %>%
        summarize(avg_correct = mean(correct, na.rm = TRUE)) %>%
        ggplot(aes(x=current_arrangement,fill=prompt_img_name, y=avg_correct)) +
        geom_violin() +
        stat_summary(fun=mean, geom="point", shape=19, size=2, 
                     position=position_dodge(0.9)) +
        stat_summary(fun=median, geom="point", shape=6, size=2, position=position_dodge(0.9)) +
        facet_wrap(~phase, labeller =
                           labeller(phase = c("1" = "Phase 1","2" = "Phase 2"))) +
        theme(
                legend.position="top",
                legend.title=element_blank(),
                plot.title = element_text(size=11),
                axis.title.x=element_blank()
                ) + 
        scale_x_discrete(labels=c('Arr3','Arr4')) +
        ylab('% Correct Sessions 1&2')
        

```


## Plot phase 1 and phase 2 separately, separately for each arrangement

```{r phases-separately-arrangements, fig.width = 10}

results_table_qc_pass_ptp_analyzed_gathered %>% 
        reorder_levels(arr_phase_1_1, order = c("1", "14", "3", "15")) %>%
        ggplot(aes(x=congruency,y=ses_1_2_perf,fill=phase)) +
        geom_boxplot(width=0.5,notch=FALSE,outlier.shape = NA) + 
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.1)) +
        # stat_summary(fun=mean, geom="point", shape=20, 
        #              size=5, color="red", fill="red") +
        ylab("ses 1&2 acc") + 
        xlab('') +
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10)) + 
        scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                          name=element_blank(),
                          labels=c('Phase 1','Phase 2')) + 
        facet_wrap(~arr_phase_1_1, ncol = 4,
                   labeller = labeller(arr_phase_1_1 = c("1" = "Arr1",
                                                         "14" = "Arr2",
                                                         "3" = "Arr3",
                                                         "15" = "Arr4"))) +        
        theme(legend.position="top") + 
        scale_x_discrete(labels=c('Incongruent','Congruent')) + 
        ylab("Percent correct in sessions 1&2")



# Basic summary table
results_table_qc_pass_ptp_analyzed_gathered %>%
        reorder_levels(arr_phase_1_1, order = c("1", "14", "3", "15")) %>%
        group_by(arr_phase_1_1,congruency,phase) %>%
        get_summary_stats(ses_1_2_perf, type = 'mean_sd') %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")

```

```{r congruency-by-arrangements, message=FALSE}
results_table_qc_pass_ptp_analyzed %>%
        reorder_levels(arr_phase_1_1, order = c("1", "14", "3", "15")) %>%
        ggplot(aes(x=arr_phase_1_1,y=phase_2_min_phase_1_ses_1_2_perf,
                   fill=congruency)) + 
        geom_boxplot(width=0.5,notch = TRUE) + 
        # geom_dotplot(binaxis='y', stackdir='center',
        #              stackratio=1, dotsize=0.5, fill="black",
        #              position = position_jitterdodge(dodge.width=0.5,
        #                                              jitter.width=0.1)) +        
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.1)) +
        ylab("P2-P1, ses 1&2 acc") + 
        scale_x_discrete(labels=c('Arr1','Arr2','Arr3','Arr4')) +
        theme(axis.text.x = element_text(size=14),
              axis.text.y = element_text(size=14)) + 
        scale_fill_manual(values=c('#e5f5f9','#2ca25f')) + 
        xlab('Phase 1 arrangement')

# Basic summary table
results_table_qc_pass_ptp_analyzed %>%
        reorder_levels(arr_phase_1_1, order = c("1", "14", "3", "15")) %>%
        group_by(arr_phase_1_1,congruency) %>%
        get_summary_stats(phase_2_min_phase_1_ses_1_2_perf, type = 'mean_sd') %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")

```
# Looking at the difference between concept order?

```{r phases-separately-concepts, fig.width = 10}

results_table_qc_pass_ptp_analyzed_gathered %>% 
        ggplot(aes(x=congruency,y=ses_1_2_perf,fill=phase)) +
        geom_boxplot(width=0.5,notch=FALSE,outlier.shape = NA) + 
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.1)) +
        # xlab('') +
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10)) + 
        scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                          name=element_blank(),
                          labels=c('Phase 1','Phase 2')) + 
        facet_wrap(~concept_phase_1) +
        theme(legend.position="top") + 
        scale_x_discrete(labels=c('Incongruent','Congruent')) +
        ylab("Percent correct in sessions 1&2")

# Grid display, showing experiment by concept order
results_table_qc_pass_ptp_analyzed_gathered %>% 
        ggplot(aes(x=congruency,y=ses_1_2_perf,fill=phase)) +
        geom_boxplot(width=0.5,notch=FALSE,outlier.shape = NA) + 
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.1)) +
        # xlab('') +
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10)) + 
        scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                          name=element_blank(),
                          labels=c('Phase 1','Phase 2')) + 
        theme(legend.position="top") + 
        scale_x_discrete(labels=c('Incongruent','Congruent')) +
        ylab("Percent correct in sessions 1&2") + 
        facet_grid(arrangement_pairs ~ concept_phase_1)


# Plot just the BT, diff arrangmenets
results_table_qc_pass_ptp_analyzed_gathered %>% 
        filter(concept_phase_1 == 'beak_tail_space') %>%
        reorder_levels(arr_phase_1_1, order = c("1", "14", "3", "15")) %>%
        ggplot(aes(x=congruency,y=ses_1_2_perf,fill=phase)) +
        geom_boxplot(width=0.5,notch=FALSE,outlier.shape = NA) + 
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.1)) +
        # stat_summary(fun=mean, geom="point", shape=20, 
        #              size=5, color="red", fill="red") +
        ylab("ses 1&2 acc") + 
        xlab('') +
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10)) + 
        scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                          name=element_blank(),
                          labels=c('Phase 1','Phase 2')) + 
        facet_wrap(~arr_phase_1_1, ncol = 4,
                   labeller = labeller(arr_phase_1_1 = c("1" = "Arr1",
                                                         "14" = "Arr2",
                                                         "3" = "Arr3",
                                                         "15" = "Arr4"))) +        
        theme(legend.position="top") + 
        scale_x_discrete(labels=c('Incongruent','Congruent')) + 
        ylab("Percent correct in sessions 1&2") + 
        ggtitle('Beak Tail Space') + 
        coord_cartesian(ylim=(c(0.5,1.0)))

# Plot just the NL, diff arrangmenets
results_table_qc_pass_ptp_analyzed_gathered %>% 
        filter(concept_phase_1 == 'neck_legs_space') %>%
        reorder_levels(arr_phase_1_1, order = c("1", "14", "3", "15")) %>%
        ggplot(aes(x=congruency,y=ses_1_2_perf,fill=phase)) +
        geom_boxplot(width=0.5,notch=FALSE,outlier.shape = NA) + 
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.1)) +
        # stat_summary(fun=mean, geom="point", shape=20, 
        #              size=5, color="red", fill="red") +
        ylab("ses 1&2 acc") + 
        xlab('') +
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10)) + 
        scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                          name=element_blank(),
                          labels=c('Phase 1','Phase 2')) + 
        facet_wrap(~arr_phase_1_1, ncol = 4,
                   labeller = labeller(arr_phase_1_1 = c("1" = "Arr1",
                                                         "14" = "Arr2",
                                                         "3" = "Arr3",
                                                         "15" = "Arr4"))) +        
        theme(legend.position="top") + 
        scale_x_discrete(labels=c('Incongruent','Congruent')) + 
        ylab("Percent correct in sessions 1&2") + 
        ggtitle('Neck Legs Space') + 
        coord_cartesian(ylim=(c(0.5,1.0)))



# Basic summary table
# results_table_qc_pass_ptp_analyzed_gathered %>%
#         reorder_levels(arr_phase_1_1, order = c("1", "14", "3", "15")) %>%
#         group_by(arr_phase_1_1,congruency,phase) %>%
#         get_summary_stats(ses_1_2_perf, type = 'mean_sd') %>%
#         knitr::kable() %>%
#         kable_styling(bootstrap_options = "striped")

```

```{r grid-concept-order-arrangement, fig.width=10, fig.height=10}

# Grid display, showing arr_phase_1_1 by concept order
results_table_qc_pass_ptp_analyzed_gathered %>% 
        ggplot(aes(x=congruency,y=ses_1_2_perf,fill=phase)) +
        geom_boxplot(width=0.5,notch=FALSE,outlier.shape = NA) + 
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.05)) +
        # xlab('') +
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10)) + 
        scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                          name=element_blank(),
                          labels=c('Phase 1','Phase 2')) + 
        theme(legend.position="top") + 
        scale_x_discrete(labels=c('Incongruent','Congruent')) +
        ylab("Percent correct in sessions 1&2") + 
        facet_grid(arr_phase_1_1 ~ concept_phase_1)

```
## Look at performance for individual toys brokend down by concept order INCOMPLETE

```{r individual-targets-incongruent-expt-1-concept-order, fig.height = 5, fig.width = 10}

# Filter to have only sessions 1-2, only incongruent, phase, arrangement, and the target that was the prompt for the trial

long_form_data_qc_pass_ptp %>%
        filter(arrangement_pairs == 'arr_1_2' & 
                   (session == 1 | session == 2) & 
                   congruency == 0) %>%
        select(congruency,arr_phase_1_1,arr_phase_2_1,
               current_arrangement,concept_phase_1,ptp,
               phase,session,prompt_img_name,correct) %>%
        reorder_levels(prompt_img_name, 
                       order = c("Sledge", "Gingerman", "Bear")) %>%
        reorder_levels(current_arrangement,
                       order = c('3','15')) %>%
        group_by(concept_phase_1,current_arrangement,ptp,phase,prompt_img_name) %>%
        summarize(avg_correct = mean(correct, na.rm = TRUE)) %>%
        ggplot(aes(x=current_arrangement,fill=prompt_img_name, y=avg_correct)) +
        geom_violin() +
        stat_summary(fun=mean, geom="point", shape=19, size=2, 
                     position=position_dodge(0.9)) +
        stat_summary(fun=median, geom="point", shape=6, size=2, position=position_dodge(0.9)) +
        theme(
                legend.position="top",
                legend.title=element_blank(),
                plot.title = element_text(size=11),
                axis.title.x=element_blank()
                ) + 
        # scale_x_discrete(labels=c('Arr3','Arr4')) +
        ylab('% Correct Sessions 1&2') + 
        facet_wrap(~phase) 
        

```



```{r phase-1-concept-diff-by-arrangement, fig.width=15}


# Just phase 1 data for sessions 1 and 2, by arrangement order
results_table_qc_pass_ptp_analyzed %>%
        ggplot(aes(x=arr_phase_1_1,y=phase_1_ses_1_2_perf,fill=concept_phase_1)) + 
        geom_boxplot(width=0.5,outlier.shape = NA) + 
        # geom_dotplot(binaxis='y', stackdir='center',
        #              stackratio=1, dotsize=0.5, fill="black") +
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.1)) +    
        # stat_summary(fun=mean, geom="point", shape=20, size=5, color="red", fill="red") +
        ylab("Phase 1, ses 1&2 acc") + 
        # xlab('Arrangement for Phase 1') + 
        # scale_x_discrete(labels=c('Arr1','Arr2','Arr3','Arr4')) +
        # coord_cartesian(ylim=(c(0.8,0.9))) +
        theme(axis.text.x = element_text(size=14),
              axis.text.y = element_text(size=14)) +
        facet_wrap(~congruency)
        # ggtitle("Phase 1 scores, Arrangement Order")


# Basic summary table
results_table_qc_pass_ptp_analyzed %>%
        group_by(congruency,arr_phase_1_1,concept_phase_1) %>%
        get_summary_stats(phase_1_ses_1_2_perf, type = 'median') %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")


```

