---
title: "thesis_writeup"
output: bookdown::html_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load-all-libraries, message=FALSE, warning=FALSE, results=FALSE}

# Clean the environment
rm(list=ls())

# Load libraries
library(tidyverse)
library(readxl)
library(ggpubr)
library(rstatix)
library(emmeans)
library(BayesFactor)
library(DT)
library(kableExtra)
library(assortedRFunctions)
library(TOSTER)

# Source other scripts
source('./utils/load_transform_gather.R')

```

# Load and get the datasets ready

```{r load-transform-gather-filter-qc, message=FALSE}

outList <- load_transform_gather()

long_form_data_all_ptp_analyzed <- 
    outList$long_form_data_all_ptp_analyzed
long_form_data_qc_pass_ptp_analyzed <- 
    outList$long_form_data_qc_pass_ptp_analyzed

results_table_all_ptp_analyzed <- 
        outList$results_table_all_ptp_analyzed
results_table_qc_pass_ptp_analyzed <- 
    outList$results_table_qc_pass_ptp_analyzed
results_table_qc_pass_ptp_analyzed_gathered <- 
    outList$results_table_qc_pass_ptp_analyzed_gathered

rm(outList)

```



# Plots for experiment 1:


```{r define-flags}

which_expt <- 1

```


## The Basic congruency effect:

```{r congruency-effect-expt-1, fig.width=3, fig.height=3}

results_table_qc_pass_ptp_analyzed %>%
        filter(experiment == which_expt) %>%
        ggplot(aes(x=congruency,
                   y=phase_2_min_phase_1_ses_1_2_perf,
                   fill=congruency)) + 
        geom_boxplot(width=0.6,notch = TRUE,outlier.shape = NA) + 
        # geom_point(pch=21,
        #            position = position_jitterdodge(dodge.width=0.5,
        #                                            jitter.width=0.1)) +
        geom_dotplot(binaxis='y', stackdir='center',
                     stackratio=1, dotsize=0.6, fill="black") +
        stat_summary(fun=mean, geom="point", shape=20, size=5, color="red", fill="red") +    
        ylab("Plase 2 - Phase 1") + 
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10)) +
        scale_x_discrete(labels=c('Incongruent','Congruent')) +
        scale_fill_manual(values=c('#e5f5f9','#2ca25f')) + 
        theme(legend.position="none",
              axis.title.x=element_blank())

# Basic summary table
results_table_qc_pass_ptp_analyzed %>%
        filter(experiment == which_expt) %>%
        group_by(congruency) %>%
        get_summary_stats(phase_2_min_phase_1_ses_1_2_perf, type = 'mean_sd') %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")

# Bayes factor analysis:

# Analyze session differences
ses_1_2_perf_congruent_1_arr_1_2 <-
    results_table_qc_pass_ptp_analyzed %>%
    filter(experiment == which_expt & congruency == 1) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]

ses_1_2_perf_congruent_0_arr_1_2 <-
    results_table_qc_pass_ptp_analyzed %>%
    filter(experiment == which_expt & congruency == 0) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]

bf_ses_1_2_perf_arr_1_2 <-
    reportBF(ttestBF(
        ses_1_2_perf_congruent_1_arr_1_2,
        ses_1_2_perf_congruent_0_arr_1_2,
        paired = FALSE
    ),
    4)

# Basic t-test
t.test(ses_1_2_perf_congruent_0_arr_1_2,ses_1_2_perf_congruent_1_arr_1_2,paired=FALSE)

# Effect size for the session differences
sd_c1 <- sd(ses_1_2_perf_congruent_1_arr_1_2)
sd_c0 <- sd(ses_1_2_perf_congruent_0_arr_1_2)

n_c1 <- length(ses_1_2_perf_congruent_1_arr_1_2)
n_c0 <- length(ses_1_2_perf_congruent_0_arr_1_2)

pooled_sd <- sqrt( 
    (
    (n_c1-1)*(sd_c1^2) + 
    (n_c0-1)*(sd_c0^2)
    ) / (n_c1 + n_c0 - 2)
    )

effect_size_arr_1_2 <- (mean(ses_1_2_perf_congruent_1_arr_1_2) - mean(ses_1_2_perf_congruent_0_arr_1_2)) /
    pooled_sd

```





## The basic congruency effect, broken in phases

```{r congruency-effect-expt-1-by-phases, fig.width=5}
results_table_qc_pass_ptp_analyzed_gathered %>% 
        filter(experiment == which_expt) %>%
        ggplot(aes(x=congruency,
                   y=ses_1_2_perf,
                   fill=phase)) +
        geom_boxplot(width=0.5,notch=TRUE,outlier.shape = NA) + 
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.05)) +
        ylab("Percent correct in sessions 1&2") + 
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10),
              axis.title.x=element_blank(),
              legend.position = 'top') + 
        scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                          name=element_blank(),
                          labels=c('Phase 1','Phase 2')) + 
        scale_x_discrete(labels=c('Incongruent','Congruent'))

# Basic summary table
results_table_qc_pass_ptp_analyzed_gathered %>%
        filter(experiment == which_expt) %>%
        group_by(congruency,phase) %>%
        get_summary_stats(ses_1_2_perf, type = 'mean_sd') %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")
```


## The Basic congruency effect, arrangement order:

```{r congruency-effect-expt-1-by-arrangements, fig.width=5}

results_table_qc_pass_ptp_analyzed %>%
        filter(experiment == which_expt) %>%
        ggplot(aes(x=congruency,
                   y=phase_2_min_phase_1_ses_1_2_perf,
                   fill=congruency)) + 
        geom_boxplot(width=0.5,notch = TRUE,outlier.shape = NA) + 
        # geom_point(pch=21,
        #            position = position_jitterdodge(dodge.width=0.5,
        #                                            jitter.width=0.1)) +
        geom_dotplot(binaxis='y', stackdir='center',
                     stackratio=1, dotsize=0.7, fill="black") +
        stat_summary(fun=mean, geom="point", shape=20, size=5, color="red", fill="red") +    
        ylab("Plase 2 - Phase 1") + 
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10)) +
        scale_x_discrete(labels=c('Incongruent','Congruent')) +
        scale_fill_manual(values=c('#e5f5f9','#2ca25f')) + 
        theme(legend.position="none",
              axis.title.x=element_blank()) + 
        facet_wrap(~arr_phase_1_name,
                   labeller = labeller(arr_phase_1_name = c("1" = "Start with Arr1",
                                                         "2" = "Start with Arr2")))

# Basic summary table
results_table_qc_pass_ptp_analyzed %>%
        filter(experiment == which_expt) %>%
        group_by(arr_phase_1_name,congruency) %>%
        get_summary_stats(phase_2_min_phase_1_ses_1_2_perf, type = 'mean_sd') %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")

# Bayes factor analysis

data_arr_1_c1 <- results_table_qc_pass_ptp_analyzed %>%
    filter(arr_phase_1_name == 1 & congruency == 1) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]
data_arr_1_c0 <- results_table_qc_pass_ptp_analyzed %>%
    filter(arr_phase_1_name == 1 & congruency == 0) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]
data_arr_2_c1 <- results_table_qc_pass_ptp_analyzed %>%
    filter(arr_phase_1_name == 2 & congruency == 1) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]
data_arr_2_c0 <- results_table_qc_pass_ptp_analyzed %>%
    filter(arr_phase_1_name == 2 & congruency == 0) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]

# Run the bayesian analysis

BF_arr_1_first <- ttestBF(
    data_arr_1_c1,data_arr_1_c0,    
    paired = FALSE
) %>% reportBF(4)
BF_arr_2_first <- ttestBF(
    data_arr_2_c1,
    data_arr_2_c0,    
    paired = FALSE
) %>% reportBF(4)


```
## The basic congruency effect, broken in phases, arrangement order

```{r congruency-effect-expt-1-by-phases-by-arrangements, fig.width=5}
results_table_qc_pass_ptp_analyzed_gathered %>% 
        filter(experiment == which_expt) %>%
        ggplot(aes(x=congruency,
                   y=ses_1_2_perf,
                   fill=phase)) +
        geom_boxplot(width=0.5,notch=TRUE,outlier.shape = NA) + 
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.05)) +
        ylab("Percent correct in sessions 1&2") + 
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10),
              axis.title.x=element_blank(),
              legend.position = 'top') + 
        scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                          name=element_blank(),
                          labels=c('Phase 1','Phase 2')) + 
        scale_x_discrete(labels=c('Incongruent','Congruent')) + 
        facet_wrap(~arr_phase_1_name,
                   labeller = labeller(arr_phase_1_name = c("1" = "Start with Arr1",
                                                 "2" = "Start with Arr2")))

# Basic summary table
results_table_qc_pass_ptp_analyzed_gathered %>%
        group_by(experiment,congruency,phase) %>%
        get_summary_stats(ses_1_2_perf, type = 'mean_sd') %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")
```


## Look at performance for individual toys

```{r individual-targets-incongruent-expt-1, fig.height = 5, fig.width = 10}

# Filter to have only sessions 1-2, only incongruent, phase, arrangement, and 
# the target that was the prompt for the trial

long_form_data_qc_pass_ptp_analyzed %>%
        filter(experiment == which_expt & 
                       (session == 1 | session == 2) & 
                       congruency == 0) %>%
        select(congruency,arr_phase_1_name,arr_phase_2_name,
               current_arrangement,concept_phase_1,ptp,
               phase,session,prompt_img_name,correct) %>%
        reorder_levels(prompt_img_name, 
                       order = c("Sledge", "Gingerman", "Bear")) %>%
        reorder_levels(current_arrangement,
                       order = c('1','2')) %>%
        group_by(current_arrangement,ptp,phase,prompt_img_name) %>%
        summarize(avg_correct = mean(correct, na.rm = TRUE)) %>%
        ggplot(aes(x=current_arrangement,fill=prompt_img_name, y=avg_correct)) +
        geom_violin() +
        stat_summary(fun=mean, geom="point", shape=19, size=2, 
                     position=position_dodge(0.9)) +
        stat_summary(fun=median, geom="point", shape=6, size=2, position=position_dodge(0.9)) +
        facet_wrap(~phase, labeller =
                           labeller(phase = c("1" = "Phase 1","2" = "Phase 2"))) +
        theme(
                legend.position="top",
                legend.title=element_blank(),
                plot.title = element_text(size=11),
                axis.text.x = element_text(size=11),
                axis.text.y = element_text(size=11)
                ) +        
        scale_x_discrete(labels=c('Arr1','Arr2')) +
        ylab('% Correct Sessions 1&2') + 
        xlab('Arrangement in this phase')
        

```











## ANOVA 3-way: congruency, concept order, arrangement order

```{r expt1-anova-3-way}

# Compute the mean and the standard deviation (SD) of pain_score by groups:
results_table_qc_pass_ptp_analyzed %>%  
        filter(experiment == which_expt) %>%
        group_by(congruency, arr_phase_1_name, concept_phase_1) %>%
        get_summary_stats(phase_2_min_phase_1_ses_1_2_perf, type = "mean_sd")

# Identify outliers
results_table_qc_pass_ptp_analyzed %>%  
        filter(experiment == which_expt) %>%
        group_by(congruency, arr_phase_1_name, concept_phase_1) %>%
        identify_outliers(phase_2_min_phase_1_ses_1_2_perf)

# Normality tests and assumptions
model  <- results_table_qc_pass_ptp_analyzed %>%
        filter(experiment == which_expt) %>%
        lm(phase_2_min_phase_1_ses_1_2_perf ~ 
                     congruency*
                     arr_phase_1_name*
                     concept_phase_1, data = .)

# QQ plot
ggqqplot(residuals(model))

# Create a QQ plot of residuals
ggqqplot(residuals(model))

# Compute Shapiro-Wilk test of normality
shapiro_test(residuals(model))

# QQ plots for each cell
results_table_qc_pass_ptp_analyzed %>%  
        filter(experiment == which_expt) %>%
        group_by(congruency, arr_phase_1_name, concept_phase_1) %>%
        ggqqplot("phase_2_min_phase_1_ses_1_2_perf", ggtheme = theme_bw()) +
        facet_grid(congruency + concept_phase_1 ~ arr_phase_1_name, 
                   labeller = "label_both")

# Homogeneity of variance
results_table_qc_pass_ptp_analyzed %>%  
        filter(experiment == which_expt) %>%
        levene_test(phase_2_min_phase_1_ses_1_2_perf ~ 
                            congruency*
                            arr_phase_1_name*
                            concept_phase_1)


# Do the test of normality by each group
results_table_qc_pass_ptp_analyzed %>%  
        filter(experiment == which_expt) %>%
        group_by(congruency, arr_phase_1_name, concept_phase_1) %>%
        shapiro_test(phase_2_min_phase_1_ses_1_2_perf)



aov_3_expt_1 <- results_table_qc_pass_ptp_analyzed %>%
        filter(experiment == which_expt) %>%
        anova_test(
        phase_2_min_phase_1_ses_1_2_perf ~
                congruency*concept_phase_1*arr_phase_1_name)
aov_3_expt_1 %>%
        knitr::kable(caption = 'Expt1: congruency -X- concept -X- arrangement') %>%
        kable_styling(bootstrap_options = "striped")


```


```{r emmeans-followup}

pwc <- results_table_qc_pass_ptp_analyzed %>%
        filter(experiment == which_expt) %>%
    group_by(arr_phase_1_name) %>%
  emmeans_test(phase_2_min_phase_1_ses_1_2_perf ~ congruency, p.adjust.method = "bonferroni") 
pwc %>%
    knitr::kable(caption = 'Expt1: congruency -X- concept -X- arrangement') %>%
    kable_styling(bootstrap_options = "striped")


```
## ANOVA (Bayesian) 3-way: congruency, concept order, arrangement

```{r anova-bayesian-expt1}

data_for_bayes_anova <- results_table_qc_pass_ptp_analyzed %>% 
        filter(experiment == which_expt)

bayes_aov <- anovaBF(phase_2_min_phase_1_ses_1_2_perf~
                             congruency*
                             concept_phase_1*
                             arr_phase_1_name,
                     data = data_for_bayes_anova,
                     whichModels = 'all',
                     whichRandom = 'ptp',
                     iterations = 10000)

bayes_aov <- sort(bayes_aov, decreasing = TRUE)

bayes_aov %>% knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")

```




# Plots for experiment 2:


```{r define-flags}

which_expt <- 2

```


## The Basic congruency effect:

```{r congruency-effect-expt-2, fig.width=5}

results_table_qc_pass_ptp_analyzed %>%
        filter(experiment == which_expt) %>%
        ggplot(aes(x=congruency,
                   y=phase_2_min_phase_1_ses_1_2_perf,
                   fill=congruency)) + 
        geom_boxplot(width=0.2,notch = TRUE,outlier.shape = NA) + 
        # geom_point(pch=21,
        #            position = position_jitterdodge(dodge.width=0.5,
        #                                            jitter.width=0.1)) +
        geom_dotplot(binaxis='y', stackdir='center',
                     stackratio=1, dotsize=0.7, fill="black") +
        stat_summary(fun=mean, geom="point", shape=20, size=5, color="red", fill="red") +    
        ylab("Plase 2 - Phase 1") + 
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10)) +
        scale_x_discrete(labels=c('Incongruent','Congruent')) +
        scale_fill_manual(values=c('#e5f5f9','#2ca25f')) + 
        theme(legend.position="none",
              axis.title.x=element_blank())

# Basic summary table
results_table_qc_pass_ptp_analyzed %>%
        filter(experiment == which_expt) %>%
        group_by(congruency) %>%
        get_summary_stats(phase_2_min_phase_1_ses_1_2_perf, type = 'mean_sd') %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")

# Bayes factor analysis:

# Analyze session differences
ses_1_2_perf_congruent_1_arr_1_2 <-
    results_table_qc_pass_ptp_analyzed %>%
    filter(experiment == which_expt & congruency == 1) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]

ses_1_2_perf_congruent_0_arr_1_2 <-
    results_table_qc_pass_ptp_analyzed %>%
    filter(experiment == which_expt & congruency == 0) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]

bf_ses_1_2_perf_arr_1_2 <-
    reportBF(ttestBF(
        ses_1_2_perf_congruent_1_arr_1_2,
        ses_1_2_perf_congruent_0_arr_1_2,
        paired = FALSE
    ),
    4)

# Basic t-test
t.test(ses_1_2_perf_congruent_0_arr_1_2,ses_1_2_perf_congruent_1_arr_1_2,paired=FALSE)

# Effect size for the session differences
sd_c1 <- sd(ses_1_2_perf_congruent_1_arr_1_2)
sd_c0 <- sd(ses_1_2_perf_congruent_0_arr_1_2)

n_c1 <- length(ses_1_2_perf_congruent_1_arr_1_2)
n_c0 <- length(ses_1_2_perf_congruent_0_arr_1_2)

pooled_sd <- sqrt( 
    (
    (n_c1-1)*(sd_c1^2) + 
    (n_c0-1)*(sd_c0^2)
    ) / (n_c1 + n_c0 - 2)
    )

effect_size_arr_1_2 <- (mean(ses_1_2_perf_congruent_1_arr_1_2) - mean(ses_1_2_perf_congruent_0_arr_1_2)) /
    pooled_sd

```





## The basic congruency effect, broken in phases

```{r congruency-effect-expt-2-by-phases, fig.width=5}
results_table_qc_pass_ptp_analyzed_gathered %>% 
        filter(experiment == which_expt) %>%
        ggplot(aes(x=congruency,
                   y=ses_1_2_perf,
                   fill=phase)) +
        geom_boxplot(width=0.5,notch=TRUE,outlier.shape = NA) + 
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.05)) +
        ylab("Percent correct in sessions 1&2") + 
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10),
              axis.title.x=element_blank(),
              legend.position = 'top') + 
        scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                          name=element_blank(),
                          labels=c('Phase 1','Phase 2')) + 
        scale_x_discrete(labels=c('Incongruent','Congruent'))

# Basic summary table
results_table_qc_pass_ptp_analyzed_gathered %>%
        filter(experiment == which_expt) %>%
        group_by(congruency,phase) %>%
        get_summary_stats(ses_1_2_perf, type = 'mean_sd') %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")
```


## The Basic congruency effect, arrangement order:

```{r congruency-effect-expt-2-by-arrangements, fig.width=5}

results_table_qc_pass_ptp_analyzed %>%
        filter(experiment == which_expt) %>%
        ggplot(aes(x=congruency,
                   y=phase_2_min_phase_1_ses_1_2_perf,
                   fill=congruency)) + 
        geom_boxplot(width=0.5,notch = TRUE,outlier.shape = NA) + 
        # geom_point(pch=21,
        #            position = position_jitterdodge(dodge.width=0.5,
        #                                            jitter.width=0.1)) +
        geom_dotplot(binaxis='y', stackdir='center',
                     stackratio=1, dotsize=0.7, fill="black") +
        stat_summary(fun=mean, geom="point", shape=20, size=5, color="red", fill="red") +    
        ylab("Plase 2 - Phase 1") + 
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10)) +
        scale_x_discrete(labels=c('Incongruent','Congruent')) +
        scale_fill_manual(values=c('#e5f5f9','#2ca25f')) + 
        theme(legend.position="none",
              axis.title.x=element_blank()) + 
        facet_wrap(~arr_phase_1_name,
                   labeller = labeller(arr_phase_1_name = c("3" = "Start with Arr3",
                                                         "4" = "Start with Arr4")))

# Basic summary table
results_table_qc_pass_ptp_analyzed %>%
        filter(experiment == which_expt) %>%
        group_by(arr_phase_1_name,congruency) %>%
        get_summary_stats(phase_2_min_phase_1_ses_1_2_perf, type = 'mean_sd') %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")

# Bayes factor analysis

data_arr_3_c1 <- results_table_qc_pass_ptp_analyzed %>%
    filter(arr_phase_1_name == 3 & congruency == 1) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]
data_arr_3_c0 <- results_table_qc_pass_ptp_analyzed %>%
    filter(arr_phase_1_name == 3 & congruency == 0) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]
data_arr_4_c1 <- results_table_qc_pass_ptp_analyzed %>%
    filter(arr_phase_1_name == 4 & congruency == 1) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]
data_arr_4_c0 <- results_table_qc_pass_ptp_analyzed %>%
    filter(arr_phase_1_name == 4 & congruency == 0) %>%
    select(phase_2_min_phase_1_ses_1_2_perf) %>% .[[1]]

# Run the bayesian analysis

BF_arr_3_first <- ttestBF(
    data_arr_3_c1,
    data_arr_3_c0,    
    paired = FALSE
) %>% reportBF(4)
BF_arr_4_first <- ttestBF(
    data_arr_4_c1,
    data_arr_4_c0,    
    paired = FALSE
) %>% reportBF(4)


```

## The basic congruency effect, broken in phases, arrangement order

```{r congruency-effect-expt-2-by-phases-by-arrangements, fig.width=5}
results_table_qc_pass_ptp_analyzed_gathered %>% 
        filter(experiment == which_expt) %>%
        ggplot(aes(x=congruency,
                   y=ses_1_2_perf,
                   fill=phase)) +
        geom_boxplot(width=0.5,notch=TRUE,outlier.shape = NA) + 
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.05)) +
        ylab("Percent correct in sessions 1&2") + 
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10),
              axis.title.x=element_blank(),
              legend.position = 'top') + 
        scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                          name=element_blank(),
                          labels=c('Phase 1','Phase 2')) + 
        scale_x_discrete(labels=c('Incongruent','Congruent')) + 
        facet_wrap(~arr_phase_1_name,
                   labeller = labeller(arr_phase_1_name = c("3" = "Start with Arr3",
                                                 "4" = "Start with Arr4")))

# Basic summary table
results_table_qc_pass_ptp_analyzed_gathered %>%
        group_by(experiment,congruency,phase) %>%
        get_summary_stats(ses_1_2_perf, type = 'mean_sd') %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")
```


## Look at performance for individual toys

```{r individual-targets-incongruent-expt-2, fig.height = 5, fig.width = 10}

# Filter to have only sessions 1-2, only incongruent, phase, arrangement, and 
# the target that was the prompt for the trial

long_form_data_qc_pass_ptp_analyzed %>%
        filter(experiment == which_expt & 
                       (session == 1 | session == 2) & 
                       congruency == 0) %>%
        select(congruency,arr_phase_1_name,arr_phase_2_name,
               current_arrangement,concept_phase_1,ptp,
               phase,session,prompt_img_name,correct) %>%
        reorder_levels(prompt_img_name, 
                       order = c("Sledge", "Gingerman", "Bear")) %>%
        reorder_levels(current_arrangement,
                       order = c('3','4')) %>%
        group_by(current_arrangement,ptp,phase,prompt_img_name) %>%
        summarize(avg_correct = mean(correct, na.rm = TRUE)) %>%
        ggplot(aes(x=current_arrangement,fill=prompt_img_name, y=avg_correct)) +
        geom_violin() +
        stat_summary(fun=mean, geom="point", shape=19, size=2, 
                     position=position_dodge(0.9)) +
        stat_summary(fun=median, geom="point", shape=6, size=2, position=position_dodge(0.9)) +
        facet_wrap(~phase, labeller =
                           labeller(phase = c("1" = "Phase 1","2" = "Phase 2"))) +
        theme(
                legend.position="top",
                legend.title=element_blank(),
                plot.title = element_text(size=11),
                axis.text.x = element_text(size=11),
                axis.text.y = element_text(size=11)
                ) +        
        scale_x_discrete(labels=c('Arr3','Arr4')) +
        ylab('% Correct Sessions 1&2') + 
        xlab('Arrangement in this phase')
        

```

## ANOVA (Bayesian) 3-way: congruency, concept order, arrangement

```{r anova-bayesian-expt2}

data_for_bayes_anova <- results_table_qc_pass_ptp_analyzed %>% 
        filter(experiment == which_expt)

bayes_aov <- anovaBF(phase_2_min_phase_1_ses_1_2_perf~
                             congruency*
                             concept_phase_1*
                             arr_phase_1_name,
                     data = data_for_bayes_anova,
                     whichModels = 'withmain',
                     whichRandom = 'ptp',
                     iterations = 100000)

bayes_aov <- sort(bayes_aov, decreasing = TRUE)

bayes_aov %>% knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")

```


## OLD Plot phase 1 and phase 2 separately, separately for each arrangement

```{r phases-separately-arrangements, fig.width = 10}

results_table_qc_pass_ptp_analyzed_gathered %>% 
        reorder_levels(arr_phase_1_1, order = c("1", "14", "3", "15")) %>%
        ggplot(aes(x=congruency,y=ses_1_2_perf,fill=phase)) +
        geom_boxplot(width=0.5,notch=FALSE,outlier.shape = NA) + 
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.1)) +
        # stat_summary(fun=mean, geom="point", shape=20, 
        #              size=5, color="red", fill="red") +
        ylab("ses 1&2 acc") + 
        xlab('') +
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10)) + 
        scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                          name=element_blank(),
                          labels=c('Phase 1','Phase 2')) + 
        facet_wrap(~arr_phase_1_1, ncol = 4,
                   labeller = labeller(arr_phase_1_1 = c("1" = "Arr1",
                                                         "14" = "Arr2",
                                                         "3" = "Arr3",
                                                         "15" = "Arr4"))) +        
        theme(legend.position="top") + 
        scale_x_discrete(labels=c('Incongruent','Congruent')) + 
        ylab("Percent correct in sessions 1&2")



# Basic summary table
results_table_qc_pass_ptp_analyzed_gathered %>%
        reorder_levels(arr_phase_1_1, order = c("1", "14", "3", "15")) %>%
        group_by(arr_phase_1_1,congruency,phase) %>%
        get_summary_stats(ses_1_2_perf, type = 'mean_sd') %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")

```



```{r congruency-by-arrangements, message=FALSE}
results_table_qc_pass_ptp_analyzed %>%
        reorder_levels(arr_phase_1_1, order = c("1", "14", "3", "15")) %>%
        ggplot(aes(x=arr_phase_1_1,y=phase_2_min_phase_1_ses_1_2_perf,
                   fill=congruency)) + 
        geom_boxplot(width=0.5,notch = TRUE) + 
        # geom_dotplot(binaxis='y', stackdir='center',
        #              stackratio=1, dotsize=0.5, fill="black",
        #              position = position_jitterdodge(dodge.width=0.5,
        #                                              jitter.width=0.1)) +        
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.1)) +
        ylab("P2-P1, ses 1&2 acc") + 
        scale_x_discrete(labels=c('Arr1','Arr2','Arr3','Arr4')) +
        theme(axis.text.x = element_text(size=14),
              axis.text.y = element_text(size=14)) + 
        scale_fill_manual(values=c('#e5f5f9','#2ca25f')) + 
        xlab('Phase 1 arrangement')

# Basic summary table
results_table_qc_pass_ptp_analyzed %>%
        reorder_levels(arr_phase_1_1, order = c("1", "14", "3", "15")) %>%
        group_by(arr_phase_1_1,congruency) %>%
        get_summary_stats(phase_2_min_phase_1_ses_1_2_perf, type = 'mean_sd') %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")

```

# Looking at the difference between concept order?

```{r phases-separately-concepts, fig.width = 10}

results_table_qc_pass_ptp_analyzed_gathered %>% 
        ggplot(aes(x=congruency,y=ses_1_2_perf,fill=phase)) +
        geom_boxplot(width=0.5,notch=FALSE,outlier.shape = NA) + 
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.1)) +
        # xlab('') +
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10)) + 
        scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                          name=element_blank(),
                          labels=c('Phase 1','Phase 2')) + 
        facet_wrap(~concept_phase_1) +
        theme(legend.position="top") + 
        scale_x_discrete(labels=c('Incongruent','Congruent')) +
        ylab("Percent correct in sessions 1&2")

# Grid display, showing experiment by concept order
results_table_qc_pass_ptp_analyzed_gathered %>% 
        ggplot(aes(x=congruency,y=ses_1_2_perf,fill=phase)) +
        geom_boxplot(width=0.5,notch=FALSE,outlier.shape = NA) + 
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.1)) +
        # xlab('') +
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10)) + 
        scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                          name=element_blank(),
                          labels=c('Phase 1','Phase 2')) + 
        theme(legend.position="top") + 
        scale_x_discrete(labels=c('Incongruent','Congruent')) +
        ylab("Percent correct in sessions 1&2") + 
        facet_grid(arrangement_pairs ~ concept_phase_1)


# Plot just the BT, diff arrangmenets
results_table_qc_pass_ptp_analyzed_gathered %>% 
        filter(concept_phase_1 == 'beak_tail_space') %>%
        reorder_levels(arr_phase_1_1, order = c("1", "14", "3", "15")) %>%
        ggplot(aes(x=congruency,y=ses_1_2_perf,fill=phase)) +
        geom_boxplot(width=0.5,notch=FALSE,outlier.shape = NA) + 
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.1)) +
        # stat_summary(fun=mean, geom="point", shape=20, 
        #              size=5, color="red", fill="red") +
        ylab("ses 1&2 acc") + 
        xlab('') +
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10)) + 
        scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                          name=element_blank(),
                          labels=c('Phase 1','Phase 2')) + 
        facet_wrap(~arr_phase_1_1, ncol = 4,
                   labeller = labeller(arr_phase_1_1 = c("1" = "Arr1",
                                                         "14" = "Arr2",
                                                         "3" = "Arr3",
                                                         "15" = "Arr4"))) +        
        theme(legend.position="top") + 
        scale_x_discrete(labels=c('Incongruent','Congruent')) + 
        ylab("Percent correct in sessions 1&2") + 
        ggtitle('Beak Tail Space') + 
        coord_cartesian(ylim=(c(0.5,1.0)))

# Plot just the NL, diff arrangmenets
results_table_qc_pass_ptp_analyzed_gathered %>% 
        filter(concept_phase_1 == 'neck_legs_space') %>%
        reorder_levels(arr_phase_1_1, order = c("1", "14", "3", "15")) %>%
        ggplot(aes(x=congruency,y=ses_1_2_perf,fill=phase)) +
        geom_boxplot(width=0.5,notch=FALSE,outlier.shape = NA) + 
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.1)) +
        # stat_summary(fun=mean, geom="point", shape=20, 
        #              size=5, color="red", fill="red") +
        ylab("ses 1&2 acc") + 
        xlab('') +
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10)) + 
        scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                          name=element_blank(),
                          labels=c('Phase 1','Phase 2')) + 
        facet_wrap(~arr_phase_1_1, ncol = 4,
                   labeller = labeller(arr_phase_1_1 = c("1" = "Arr1",
                                                         "14" = "Arr2",
                                                         "3" = "Arr3",
                                                         "15" = "Arr4"))) +        
        theme(legend.position="top") + 
        scale_x_discrete(labels=c('Incongruent','Congruent')) + 
        ylab("Percent correct in sessions 1&2") + 
        ggtitle('Neck Legs Space') + 
        coord_cartesian(ylim=(c(0.5,1.0)))



# Basic summary table
# results_table_qc_pass_ptp_analyzed_gathered %>%
#         reorder_levels(arr_phase_1_1, order = c("1", "14", "3", "15")) %>%
#         group_by(arr_phase_1_1,congruency,phase) %>%
#         get_summary_stats(ses_1_2_perf, type = 'mean_sd') %>%
#         knitr::kable() %>%
#         kable_styling(bootstrap_options = "striped")

```

```{r grid-concept-order-arrangement, fig.width=10, fig.height=10}

# Grid display, showing arr_phase_1_1 by concept order
results_table_qc_pass_ptp_analyzed_gathered %>% 
        ggplot(aes(x=congruency,y=ses_1_2_perf,fill=phase)) +
        geom_boxplot(width=0.5,notch=FALSE,outlier.shape = NA) + 
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.05)) +
        # xlab('') +
        theme(axis.text.x = element_text(size=10),
              axis.text.y = element_text(size=10)) + 
        scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                          name=element_blank(),
                          labels=c('Phase 1','Phase 2')) + 
        theme(legend.position="top") + 
        scale_x_discrete(labels=c('Incongruent','Congruent')) +
        ylab("Percent correct in sessions 1&2") + 
        facet_grid(arr_phase_1_1 ~ concept_phase_1)

```
## Look at performance for individual toys brokend down by concept order INCOMPLETE

```{r individual-targets-incongruent-expt-1-concept-order, fig.height = 5, fig.width = 10}

# Filter to have only sessions 1-2, only incongruent, phase, arrangement, and the target that was the prompt for the trial

long_form_data_qc_pass_ptp %>%
        filter(experiment == which_expt & 
                   (session == 1 | session == 2) & 
                   congruency == 0) %>%
        select(congruency,arr_phase_1_1,arr_phase_2_1,
               current_arrangement,concept_phase_1,ptp,
               phase,session,prompt_img_name,correct) %>%
        reorder_levels(prompt_img_name, 
                       order = c("Sledge", "Gingerman", "Bear")) %>%
        reorder_levels(current_arrangement,
                       order = c('3','15')) %>%
        group_by(concept_phase_1,current_arrangement,ptp,phase,prompt_img_name) %>%
        summarize(avg_correct = mean(correct, na.rm = TRUE)) %>%
        ggplot(aes(x=current_arrangement,fill=prompt_img_name, y=avg_correct)) +
        geom_violin() +
        stat_summary(fun=mean, geom="point", shape=19, size=2, 
                     position=position_dodge(0.9)) +
        stat_summary(fun=median, geom="point", shape=6, size=2, position=position_dodge(0.9)) +
        theme(
                legend.position="top",
                legend.title=element_blank(),
                plot.title = element_text(size=11),
                axis.title.x=element_blank()
                ) + 
        # scale_x_discrete(labels=c('Arr3','Arr4')) +
        ylab('% Correct Sessions 1&2') + 
        facet_wrap(~phase) 
        

```



```{r phase-1-concept-diff-by-arrangement, fig.width=15}


# Just phase 1 data for sessions 1 and 2, by arrangement order
results_table_qc_pass_ptp_analyzed %>%
        ggplot(aes(x=arr_phase_1_1,y=phase_1_ses_1_2_perf,fill=concept_phase_1)) + 
        geom_boxplot(width=0.5,outlier.shape = NA) + 
        # geom_dotplot(binaxis='y', stackdir='center',
        #              stackratio=1, dotsize=0.5, fill="black") +
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.1)) +    
        # stat_summary(fun=mean, geom="point", shape=20, size=5, color="red", fill="red") +
        ylab("Phase 1, ses 1&2 acc") + 
        # xlab('Arrangement for Phase 1') + 
        # scale_x_discrete(labels=c('Arr1','Arr2','Arr3','Arr4')) +
        # coord_cartesian(ylim=(c(0.8,0.9))) +
        theme(axis.text.x = element_text(size=14),
              axis.text.y = element_text(size=14)) +
        facet_wrap(~congruency)
        # ggtitle("Phase 1 scores, Arrangement Order")


# Basic summary table
results_table_qc_pass_ptp_analyzed %>%
        group_by(congruency,arr_phase_1_1,concept_phase_1) %>%
        get_summary_stats(phase_1_ses_1_2_perf, type = 'median') %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")


```

