---
title: "various_analyses"
output: bookdown::html_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load-all-libraries, message=FALSE, warning=FALSE, results=FALSE}

# Clean the environment
rm(list=ls())

# Load libraries
library(tidyverse)
library(readxl)
library(ggpubr)
library(rstatix)
library(emmeans)
library(BayesFactor)
library(DT)
library(kableExtra)
library(assortedRFunctions)
library(TOSTER)
library(gridExtra)

# Source other scripts
source('./utils/load_transform_gather.R')

```

# Load and get the datasets ready

```{r load-transform-gather-filter-qc}

outList <- load_transform_gather()

long_form_data_all_ptp <- 
    outList$long_form_data_all_ptp

long_form_data_qc_pass_ptp <- 
    outList$long_form_data_qc_pass_ptp

results_table_qc_pass_ptp_analyzed <- 
    outList$results_table_qc_pass_ptp_analyzed
results_table_qc_pass_ptp_analyzed_gathered <- 
    outList$results_table_qc_pass_ptp_analyzed_gathered

rm(outList)

```

# Compare arrangements for their difficulty in phase 1

## Replot all the arrangements in phase 1
```{r phase-1-arrangement-order}

# Just phase 1 data for sessions 1 and 2, by arrangement order
results_table_qc_pass_ptp_analyzed %>%
        ggplot(aes(x=arr_phase_1_1,y=phase_1_ses_1_2_perf)) + 
        geom_boxplot(width=0.5,notch = TRUE) + 
        # geom_jitter(width=0.1) + 
        geom_dotplot(binaxis='y', stackdir='center',
                     stackratio=1, dotsize=0.5, fill="black") +
        stat_summary(fun=mean, geom="point", shape=20, size=5, color="red", fill="red") +
        ylab("Phase 1, ses 1&2 acc") + 
        scale_x_discrete(labels=c('Arr1','Arr2','Arr3','Arr4')) +
        # coord_cartesian(ylim=(c(0.8,0.9))) +
        theme(axis.text.x = element_text(size=14),
              axis.text.y = element_text(size=14)) + 
        ggtitle("Phase 1 scores, Arrangement Order")

# A table showing the data
results_table_qc_pass_ptp_analyzed %>%
    group_by(arr_phase_1_1) %>%
    get_summary_stats(phase_1_ses_1_2_perf, type = 'mean_sd') %>%
    knitr::kable() %>%
    kable_styling(bootstrap_options = "striped")

```


## Compare arr3 and arr4 for phase 1, are they reliably different? 

I perform an equivalence test which will simultaneously test (a) whether the effect is significantly different from zero and (b) whether its statistically equivalent to some range of minimally interesting effect sizes.

I'm not exactly sure what the maximum difference should be between phase 1 arr3 and arr4 scores, such that it would not be a problem.

Think how many more correct responses for arr3 vs arr4 we would consider to be a problem? We are calculating performance over 2 sessions for each phase, that is 82 trials total. Lets say arr2 vs arr4 differ by 4 correct responses in phase 1, that is 4*100/82=4.878% difference in accuracy. So, if our data show that arr3 vs arr4 differ by an amount that is statistically lower than 4.878, then we'd be happy. 

Another approach for determining the maximum allowed difference would be to look at how much do people improve from phase 1 to phase 2 in the congruent case, how many more toys to they correctly respond do. Phase 2 must surely be better than phase 1 for congruent case, so people's improvements there will tell us the ballpark range for expected difference between an "easy" and "harder" arrangements. Below, you can see a table for each subcondition (but only congruent) with summary statistics for phase2 - phase1 scores. 

Minimal difference we see is 0.02 so 2% difference, for subcondition neck_legs_space & arrangement 4. That suggests 1-2 toy difference between phases, thats very low...

```{r max-allowed-diff-exporation}

results_table_qc_pass_ptp_analyzed %>%
    filter(congruency == 1) %>%
    group_by(concept_phase_1,arr_phase_1_1) %>%
    get_summary_stats(phase_2_min_phase_1_ses_1_2_perf, type = 'mean_sd') %>%
    knitr::kable() %>%
    kable_styling(bootstrap_options = "striped")
```


So for the equivalence test, I entered boundaries of 0.26 standardized difference in scores, which corresponds roughly to 0.02 raw difference in scores. 

Results show that the data is not significantly different from 0. However, the 95% confidence interval makes it clear that its consistent with a wide-range of effect sizes. So we cannot make a confident conclusion that arr3 and arr4 are not different in phase 1...

```{r arr3-arr4-phase-1-difference}

m1 <- results_table_qc_pass_ptp_analyzed %>% filter(arr_phase_1_1 == 3) %>% 
.[['phase_1_ses_1_2_perf']] %>% mean()
m2 <- results_table_qc_pass_ptp_analyzed %>% filter(arr_phase_1_1 == 15) %>% 
.[['phase_1_ses_1_2_perf']] %>% mean()

sd1 <- results_table_qc_pass_ptp_analyzed %>% filter(arr_phase_1_1 == 3) %>% 
.[['phase_1_ses_1_2_perf']] %>% sd()
sd2 <- results_table_qc_pass_ptp_analyzed %>% filter(arr_phase_1_1 == 15) %>% 
.[['phase_1_ses_1_2_perf']] %>% sd()

n1 <- results_table_qc_pass_ptp_analyzed %>% filter(arr_phase_1_1 == 3) %>% 
    nrow()
n2 <- results_table_qc_pass_ptp_analyzed %>% filter(arr_phase_1_1 == 15) %>% 
    nrow()

TOSTtwo(m1 = m1, m2 = m2, sd1 = sd1, sd2 = sd2, n1 = n1, n2 = n2, low_eqbound_d = -0.26, high_eqbound_d = 0.26)


```

## Compare arr1 and arr2 for phase 1, are they different? 

```{r arr1-arr2-phase-1-difference}

m1 <- results_table_qc_pass_ptp_analyzed %>% filter(arr_phase_1_1 == 1) %>% 
.[['phase_1_ses_1_2_perf']] %>% mean()
m2 <- results_table_qc_pass_ptp_analyzed %>% filter(arr_phase_1_1 == 14) %>% 
.[['phase_1_ses_1_2_perf']] %>% mean()

sd1 <- results_table_qc_pass_ptp_analyzed %>% filter(arr_phase_1_1 == 1) %>% 
.[['phase_1_ses_1_2_perf']] %>% sd()
sd2 <- results_table_qc_pass_ptp_analyzed %>% filter(arr_phase_1_1 == 14) %>% 
.[['phase_1_ses_1_2_perf']] %>% sd()

n1 <- results_table_qc_pass_ptp_analyzed %>% filter(arr_phase_1_1 == 1) %>% 
    nrow()
n2 <- results_table_qc_pass_ptp_analyzed %>% filter(arr_phase_1_1 == 14) %>% 
    nrow()

TOSTtwo(m1 = m1, m2 = m2, sd1 = sd1, sd2 = sd2, n1 = n1, n2 = n2, low_eqbound_d = -0.28, high_eqbound_d = 0.28)


```

## Now compare outlier vs no outlier in phase 1, maybe those are reliably different? 

```{r outlier-no-outlier-phase-1-difference}

m1 <- results_table_qc_pass_ptp_analyzed %>% filter(phase_1_lower_left_outlier == TRUE) %>% 
.[['phase_1_ses_1_2_perf']] %>% mean()
m2 <- results_table_qc_pass_ptp_analyzed %>% filter(phase_1_lower_left_outlier == FALSE) %>% 
.[['phase_1_ses_1_2_perf']] %>% mean()

sd1 <- results_table_qc_pass_ptp_analyzed %>% filter(phase_1_lower_left_outlier == TRUE) %>% 
.[['phase_1_ses_1_2_perf']] %>% sd()
sd2 <- results_table_qc_pass_ptp_analyzed %>% filter(phase_1_lower_left_outlier == FALSE) %>% 
.[['phase_1_ses_1_2_perf']] %>% sd()

n1 <- results_table_qc_pass_ptp_analyzed %>% filter(phase_1_lower_left_outlier == TRUE) %>% 
    nrow()
n2 <- results_table_qc_pass_ptp_analyzed %>% filter(phase_1_lower_left_outlier == FALSE) %>% 
    nrow()

TOSTtwo(m1 = m1, m2 = m2, sd1 = sd1, sd2 = sd2, n1 = n1, n2 = n2, low_eqbound_d = -0.27, high_eqbound_d = 0.27)


```


# Frequentist ANOVA analysis


## What if no-outlier always in phase2? Or if outlier always in phase 2?

### Separately for each phase

```{r various-analyses-12, fig.width=13, fig.height=15}

plot1 <- results_table_qc_pass_ptp_analyzed_gathered %>%
    filter(arrangement_pairs == 'arr_3_4' & arr_phase_2_1 == '3') %>%
    reorder_levels(arr_phase_1_1, order=c(3,15)) %>%
    ggplot(aes(x=arr_phase_1_1,y=ses_1_2_perf,fill=phase)) +
    geom_boxplot(width=0.5,notch = TRUE,outlier.shape = NA) + 
    geom_point(pch=21,
               position = position_jitterdodge(dodge.width=0.5,
                                               jitter.width=0.1)) +    
    scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                name='Phase',
    labels=c('Phase 1','Phase 2')) +
    xlab('Phase 1 arrangement') + 
    scale_y_continuous(name='Ses 1-2 scores',
                       breaks=seq(0.4,1,0.1),
                       limits=c(0.48,1))+
    scale_x_discrete(labels=c('Arr3 (No Outlier)','Arr4 (Outlier)')) + 
    ggtitle('Always Arr3 in phase 2') +
    theme(plot.title = element_text(hjust = 0.5),
          legend.position = 'left') + 
    annotate('text', label='3-3', x=1, y=1) +
    annotate('text', label='4-3', x=2, y=1)

plot2 <- results_table_qc_pass_ptp_analyzed_gathered %>%
    filter(arrangement_pairs == 'arr_3_4' & arr_phase_2_1 == '15') %>%
    reorder_levels(arr_phase_1_1, order=c(15,3)) %>%
    ggplot(aes(x=arr_phase_1_1,y=ses_1_2_perf,fill=phase)) +
    geom_boxplot(width=0.5,notch = TRUE,outlier.shape = NA) + 
    geom_point(pch=21,
               position = position_jitterdodge(dodge.width=0.5,
                                               jitter.width=0.1)) +    
    scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                name='Phase',
    labels=c('Phase 1','Phase 2')) +
    xlab('Phase 1 arrangement') + 
    scale_y_continuous(name='Ses 1-2 scores',
                       breaks=seq(0.4,1,0.1),
                       limits=c(0.48,1))+
    scale_x_discrete(labels=c('Arr4 (Outlier)','Arr3 (No Outlier)')) + 
    ggtitle('Always Arr4 in phase 2') +
    theme(plot.title = element_text(hjust = 0.5)) +
    annotate('text', label='4-4', x=1, y=1) +
    annotate('text', label='3-4', x=2, y=1)    

plot3 <- results_table_qc_pass_ptp_analyzed_gathered %>%
    filter(arrangement_pairs == 'arr_1_2' & arr_phase_2_1 == '14') %>%
    reorder_levels(arr_phase_1_1, order=c(14,1)) %>%
    ggplot(aes(x=arr_phase_1_1,y=ses_1_2_perf,fill=phase)) +
    geom_boxplot(width=0.5,notch = TRUE,outlier.shape = NA) + 
    geom_point(pch=21,
               position = position_jitterdodge(dodge.width=0.5,
                                               jitter.width=0.1)) +    
    scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                name='Phase',
    labels=c('Phase 1','Phase 2')) +
    xlab('Phase 1 arrangement') + 
    scale_y_continuous(name='Ses 1-2 scores',
                       breaks=seq(0.4,1,0.1),
                       limits=c(0.48,1))+
    scale_x_discrete(labels=c('Arr2 (No Outlier)','Arr1 (Outlier)')) + 
    ggtitle('Always Arr2 in phase 2') +
    theme(plot.title = element_text(hjust = 0.5),
          legend.position = 'left') + 
    annotate('text', label='2-2', x=1, y=1) +
    annotate('text', label='1-2', x=2, y=1) 

plot4 <- results_table_qc_pass_ptp_analyzed_gathered %>%
    filter(arrangement_pairs == 'arr_1_2' & arr_phase_2_1 == '1') %>%
    reorder_levels(arr_phase_1_1, order=c(1,14)) %>%
    ggplot(aes(x=arr_phase_1_1,y=ses_1_2_perf,fill=phase)) +
    geom_boxplot(width=0.5,notch = TRUE,outlier.shape = NA) + 
    geom_point(pch=21,
               position = position_jitterdodge(dodge.width=0.5,
                                               jitter.width=0.1)) +    
    scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                name='Phase',
    labels=c('Phase 1','Phase 2')) +
    xlab('Phase 1 arrangement') + 
    scale_y_continuous(name='Ses 1-2 scores',
                       breaks=seq(0.4,1,0.1),
                       limits=c(0.48,1))+
    scale_x_discrete(labels=c('Arr1 (Outlier)','Arr2 (No Outlier)')) + 
    ggtitle('Always Arr1 in phase 2') +
    theme(plot.title = element_text(hjust = 0.5)) + 
    annotate('text', label='1-1', x=1, y=1) +
    annotate('text', label='2-1', x=2, y=1)        


plot5 <- results_table_qc_pass_ptp_analyzed_gathered %>%
    filter(phase_2_lower_left_outlier == TRUE) %>%
    ggplot(aes(x=phase_1_lower_left_outlier,
               y=ses_1_2_perf,
               fill=phase)) +
    geom_boxplot(width=0.5,notch = TRUE,outlier.shape = NA) + 
    geom_point(pch=21,
               position = position_jitterdodge(dodge.width=0.5,
                                               jitter.width=0.1)) +    
    scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                name='Phase',
    labels=c('Phase 1','Phase 2')) +
    xlab('Phase 1 arrangement') + 
    scale_y_continuous(name='Ses 1-2 scores',
                       breaks=seq(0.4,1,0.1),
                       limits=c(0.48,1))+
    scale_x_discrete(labels=c('No Outlier','Outlier')) +
    ggtitle('Always Outlier in phase 2') +
    theme(plot.title = element_text(hjust = 0.5),
          legend.position = 'left') + 
    annotate('text', label='1-1', x=1, y=1) +
    annotate('text', label='2-1', x=2, y=1) 

plot6 <- results_table_qc_pass_ptp_analyzed_gathered %>%
    filter(phase_2_lower_left_outlier == FALSE) %>%
    ggplot(aes(x=phase_1_lower_left_outlier,
               y=ses_1_2_perf,
               fill=phase)) +
    geom_boxplot(width=0.5,notch = TRUE,outlier.shape = NA) + 
    geom_point(pch=21,
               position = position_jitterdodge(dodge.width=0.5,
                                               jitter.width=0.1)) +    
    scale_fill_manual(values=c('#045a8d','#d0d1e6'),
                name='Phase',
    labels=c('Phase 1','Phase 2')) +
    xlab('Phase 1 arrangement') + 
    scale_y_continuous(name='Ses 1-2 scores',
                       breaks=seq(0.4,1,0.1),
                       limits=c(0.48,1))+
    scale_x_discrete(labels=c('No Outlier','Outlier')) +
    ggtitle('Always No-Outlier in phase 2') +
    theme(plot.title = element_text(hjust = 0.5)) + 
    annotate('text', label='1-1', x=1, y=1) +
    annotate('text', label='2-1', x=2, y=1) 

grid.arrange(plot1, plot2, plot3, plot4, plot5, plot6, ncol=2)


```

So we're hoping to take the left scenario, with no-outlier being in phase 2 always. The right side scenario we say is bad, because when outlier comes after no-outlier, people just do very, very well! Despite it being incongruent.

### P2-P1 scores:

```{r various-analyses-11, fig.height=5, fig.width=13}

# Plot both experiments
plot7 <- results_table_qc_pass_ptp_analyzed %>%
        reorder_levels(arr_phase_2_1, order=c(1,14,3,15)) %>%
        ggplot(aes(x=arr_phase_2_1,
                   y=phase_2_min_phase_1_ses_1_2_perf,
                   fill=congruency)) + 
        geom_boxplot(width=0.5,notch = TRUE, outlier.shape = NA) + 
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.1)) +
        ylab("P2-P1, ses 1&2 acc") + 
        xlab('Phase 2') +
        scale_x_discrete(labels=c('Arr1\n(Outlier)','Arr2','Arr3','Arr4\n(Outlier)')) +
        ggtitle('For each arrangement being in Phase 2, P2-P1 scores ') +
        theme(axis.text.x = element_text(size=14),
              axis.text.y = element_text(size=14),
              legend.position = 'left',
              plot.title = element_text(hjust = 0.5)) + 
        scale_fill_manual(values=c('#e5f5f9','#2ca25f'),
                          name='Congruency',
                          labels=c('Incongruent','Congruent'))
# Basic summary table
# results_table_qc_pass_ptp_analyzed %>%
#         group_by(arr_phase_2_1,congruency) %>%
#         reorder_levels(arr_phase_2_1, order=c(1,14,3,15)) %>%
#         get_summary_stats(phase_2_min_phase_1_ses_1_2_perf, type = 'mean_sd') %>%
#         knitr::kable(caption = 'Basic summary table') %>%
#         kable_styling(bootstrap_options = "striped")

# Collapse for outlier / no-outlier
plot8 <- results_table_qc_pass_ptp_analyzed %>%
    ggplot(aes(x=phase_2_lower_left_outlier,
               y=phase_2_min_phase_1_ses_1_2_perf,
               fill=congruency)) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(pch=21,
           position = position_jitterdodge(dodge.width=0.75,
                                           jitter.width=0.2)) +
    xlab('Phase 2 was outlier') +
    ylab('P2-P1') + 
    scale_x_discrete(labels=c('No Outlier','Outlier')) +
    ggtitle('Congruency -X- outlier in phase 2\n Both experiments, P2-P1 scores ') +
    theme(plot.title = element_text(hjust = 0.5)) +
    scale_fill_manual(values=c('#e5f5f9','#2ca25f'),
                        name='Congruency',
                        labels=c('Incongruent','Congruent')) +
    theme(axis.text.x = element_text(size=14),
          axis.text.y = element_text(size=14))    

grid.arrange(plot7, plot8, ncol=2)


# A combined full ANOVA with experiment as a factor
aov_4_both_exp <- results_table_qc_pass_ptp_analyzed %>%
        anova_test(
                phase_2_min_phase_1_ses_1_2_perf ~
                        congruency*concept_phase_2*phase_2_lower_left_outlier*arrangement_pairs)
aov_4_both_exp %>%
        knitr::kable(caption = 'Full ANOVA, with factors: Experiment, congruency, concept in P2, outlier in P2') %>%
        kable_styling(bootstrap_options = "striped")


# ANOVA
aov_3_arr_1_2 <- results_table_qc_pass_ptp_analyzed %>%
        filter(arrangement_pairs == "arr_1_2") %>%
        anova_test(
        phase_2_min_phase_1_ses_1_2_perf ~
                congruency*concept_phase_2*phase_2_lower_left_outlier)
aov_3_arr_1_2 %>%
        knitr::kable(caption = 'Expt1: congruency -X- concept -X- outlier') %>%
        kable_styling(bootstrap_options = "striped")

aov_3_arr_3_4 <- results_table_qc_pass_ptp_analyzed %>%
        filter(arrangement_pairs == "arr_3_4") %>%
        anova_test(
                phase_2_min_phase_1_ses_1_2_perf ~
                        congruency*concept_phase_2*phase_2_lower_left_outlier)
aov_3_arr_3_4 %>%
        knitr::kable(caption = 'Expt2: congruency -X- concept -X- outlier') %>%
        kable_styling(bootstrap_options = "striped")

```

### Just Phase 2 scores:

```{r various-analyses-60, fig.height=5, fig.width=15}

# Plot both experiments
plot9 <- results_table_qc_pass_ptp_analyzed %>%
        reorder_levels(arr_phase_2_1, order=c(1,14,3,15)) %>%
        ggplot(aes(x=arr_phase_2_1,
                   y=phase_2_ses_1_2_perf,
                   fill=congruency)) + 
        geom_boxplot(width=0.5,notch = TRUE, outlier.shape = NA) + 
        geom_point(pch=21,
                   position = position_jitterdodge(dodge.width=0.5,
                                                   jitter.width=0.1)) +
        ylab("Phase 2 scores") + 
        xlab('Phase 2') +
        # scale_x_discrete(labels=c('Arr1\n(Outlier)','Arr2','Arr3','Arr4\n(Outlier)')) +
        # ggtitle('For each arrangement being in Phase 2, P2-P1 scores ') +
        theme(axis.text.x = element_text(size=14),
              axis.text.y = element_text(size=14),
              legend.position = 'left',
              plot.title = element_text(hjust = 0.5)) + 
        scale_fill_manual(values=c('#e5f5f9','#2ca25f'),
                          name='Congruency',
                          labels=c('Incongruent','Congruent'))

# Collapse for outlier / no-outlier
plot10 <- results_table_qc_pass_ptp_analyzed %>%
    ggplot(aes(x=phase_2_lower_left_outlier,
               y=phase_2_ses_1_2_perf,
               fill=congruency)) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(pch=21,
           position = position_jitterdodge(dodge.width=0.75,
                                           jitter.width=0.2)) +
    xlab('Phase 2 was outlier') +
    ylab('Phase 2 scores') + 
    # scale_x_discrete(labels=c('No Outlier','Outlier')) +
    ggtitle('Congruency -X- outlier in phase 2\n Both experiments, P2-P1 scores ') +
    theme(plot.title = element_text(hjust = 0.5)) +
    scale_fill_manual(values=c('#e5f5f9','#2ca25f'),
                        name='Congruency',
                        labels=c('Incongruent','Congruent')) +
    theme(axis.text.x = element_text(size=14),
          axis.text.y = element_text(size=14))    

grid.arrange(plot9, plot10, ncol=2)



# Yet another plot, here contrast outlier in phase 2 for congr vs incongr, VS no-outlier in phase 2 for congr vs incongr.
# # Rationale: outlier in phase 2 seems to be the same regardless of congr, but no-outlier in phase 2 depends on congr. So there should be an interaction
# results_table_qc_pass_ptp_analyzed %>%
#     ggplot(aes(x=phase_2_lower_left_outlier,
#                y=phase_2_ses_1_2_perf,
#                fill=congruency)) +
#     geom_boxplot(outlier.shape = NA) +
#     geom_point(pch=21,
#            position = position_jitterdodge(dodge.width=0.75,
#                                            jitter.width=0.2)) +
#     xlab('Phase 2 arrangement') +
#     scale_y_continuous(name='Phase 2 scores',
#                        breaks=seq(0.5,1,0.1),
#                        limits=c(0.55,1)) +
#     scale_x_discrete(labels=c('No Outlier','Outlier')) +
#     ggtitle('Contrasting congruency, depending on Outlier vs No-outlier being in phase 2\n Both experiments. Only Phase 2 scores') +
#     theme(plot.title = element_text(hjust = 0.5)) + 
#     scale_fill_manual(values=c('#e5f5f9','#2ca25f'),
#                         name='Congruency',
#                         labels=c('Incongruent','Congruent')) +
#     theme(axis.text.x = element_text(size=14),
#           axis.text.y = element_text(size=14))

results_table_qc_pass_ptp_analyzed %>%
    anova_test(phase_2_ses_1_2_perf ~ congruency*phase_2_lower_left_outlier*concept_phase_2*arrangement_pairs) %>%
    knitr::kable(caption = 'Congruency -X- Phase 2 outlier -X- Experiment') %>%
    kable_styling(bootstrap_options = "striped")

```

```{r various-analyses-9, fig.width=13, fig.height=5}

plot1 <- results_table_qc_pass_ptp_analyzed %>% 
    ggplot(aes(x=phase_1_lower_left_outlier,y=phase_2_ses_1_2_perf,fill=phase_2_lower_left_outlier)) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(pch=21,
           position = position_jitterdodge(dodge.width=0.7,
                                           jitter.width=0.1)) +
    xlab('Phase 1') +
    scale_y_continuous(name='Phase 2 scores',
                       breaks=seq(0.5,1,0.1),
                       limits=c(0.55,1))+    
    ggtitle('Only Phase 2 scores') + 
    theme(plot.title = element_text(hjust = 0.5),
          legend.position = 'left') + 
    scale_fill_manual(values=c('#f0f0f0','#636363'),
                        name='Phase 2',
                        labels=c('No outlier','Outlier')) +
    scale_x_discrete(labels=c('No Outlier','Outlier'))

plot2 <- results_table_qc_pass_ptp_analyzed %>% 
    ggplot(aes(x=congruency,y=phase_2_ses_1_2_perf,fill=phase_2_lower_left_outlier)) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(pch=21,
           position = position_jitterdodge(dodge.width=0.7,
                                           jitter.width=0.1)) +
    xlab('Congruency') +
    scale_y_continuous(name='Phase 2 scores',
                       breaks=seq(0.5,1,0.1),
                       limits=c(0.55,1))+    
    ggtitle('Only Phase 2 scores') + 
    theme(plot.title = element_text(hjust = 0.5)) + 
    scale_fill_manual(values=c('#f0f0f0','#636363'),
                        name='Phase 2',
                        labels=c('No outlier','Outlier')) + 
    scale_x_discrete(labels=c('Incongruent','Congruent'))

grid.arrange(plot1, plot2, ncol=2)

# Full anova
results_table_qc_pass_ptp_analyzed %>%
    anova_test(phase_2_ses_1_2_perf ~ phase_1_lower_left_outlier*phase_2_lower_left_outlier*arrangement_pairs) %>%
    knitr::kable(caption = 'Phase 1 outlier -X- Phase 2 outlier -X- Experiment') %>%
    kable_styling(bootstrap_options = "striped")

results_table_qc_pass_ptp_analyzed %>%
    anova_test(phase_2_ses_1_2_perf ~ congruency*phase_2_lower_left_outlier*arrangement_pairs) %>%
    knitr::kable(caption = 'Congruency -X- Phase 2 outlier -X- Experiment') %>%
    kable_styling(bootstrap_options = "striped")


```